### 2020-04-07 paper1.tex
recent work

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\begin{document}

\preprint{APS/123-QED}

\title{Manuscript Title:\\with Forced Linebreak}% Force line breaks with \\
\thanks{A footnote to the article title}%

\author{Ann Author}
 \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
\author{Second Author}%
 \email{Second.Author@institution.edu}
\affiliation{%
 Authors' institution and/or address\\
 This line break forced with \textbackslash\textbackslash
}%

\collaboration{MUSO Collaboration}%\noaffiliation

\author{Charlie Author}
 \homepage{http://www.Second.institution.edu/~Charlie.Author}
\affiliation{
 Second institution and/or address\\
 This line break forced% with \\
}%
\affiliation{
 Third institution, the second for Charlie Author
}%
\author{Delta Author}
\affiliation{%
 Authors' institution and/or address\\
 This line break forced with \textbackslash\textbackslash
}%

\collaboration{CLEO Collaboration}%\noaffiliation

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
An article usually includes an abstract, a concise summary of the work
covered at length in the main body of the article. 
\begin{description}
\item[Usage]
Secondary publications and information retrieval purposes.
\item[Structure]
You may use the \texttt{description} environment to structure your abstract;
use the optional argument of the \verb+\item+ command to give the category of each item. 
\end{description}
\end{abstract}

%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

%\tableofcontents

\section{\label{sec:level1}  Introduction}
\section{\label{sec:level1} Method}

\subsection{Graph Generalization}

\textbf{talk about how to map the original nanowire network on to a graph}.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\linewidth]{figure/mpl_plot}
	\caption{}
	\label{fig:mpl_plot}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.8\linewidth]{figure/graph_plot}
	\caption{}
	\label{fig:graph_plot}
\end{figure}

\subsection{\label{sec:level2} Centrality}
Centrality \textbf{Put some reference here} is an important measure that helps understand the fundamental structures and connectivities of networks. Betweenness centrality of nodes and edges in networks can demonstrate .... Meanwhile, closeness centrality of nodes can be used to interpret the ..... \cite{Newman2010}.

A variation of centrality measures based on current flow model proposed by Brandes and Fleischer \cite{Brandes2005} is employed here. As the electrical dynamics in our networks fall in the class of \textbf{random walks} (not sure about here).

The betweenness centrality of a edge in the networks can be determined by:

\begin{equation}
c_{CB}(e) = \frac{\sum \limits_{s \neq t \in V}\tau_{st}(e)}{(n-1)(n-2)},
\end{equation}

where $\tau_{st}(e)$ is the current flow through edge $e$ between nodes $s$ and $t$, while $n$ stands for number of nodes in the network.

The closeness centrality of a node in this context is structured in the same way as normal closeness centrality, with distance measured based on effective resistance rather than graphical distance. Therefore it is given by:

\begin{equation}
c_{CC}(v) = \frac{n-1}{\sum \limits_{v \neq w \in V} R(v,w)}.
\end{equation}
In the context of a unit $st$-current in the network, $R(v,w)$ represents the effective resistance between nodes $v$ and $w$.

\subsection{\label{sec:level2} Transfer Entropy}

Transfer entropy is an effective metric for information transduction ...... \textbf{cite Joe here}.

\begin{equation}
T_{Y \rightarrow X} = \sum \limits_{u_n} p(u_n) \log \frac{p(x_{n+1}| x_n^{(k)}, y_n^{(l)})}{p(x_{n+1}|x_n^{(k)})}.
\end{equation}

$n$ is a time index, $u_n$ represents the state transition tuple $(x_{n+1}, x_n^{(k)}, y_n^{(l)})$, $x_n^{(k)}, y_n^{(l)}$ represent the $k$ and $l$ past values of $x$ and $y$ up to and including time $n$. \textbf{rephrase here}.

\subsection{\label{sec:level2} Modularity}
Modularity is a network metric that ..... \textbf{talk about it here} \cite{Rubinov2009}.

Recent studies in neuro-science demonstrated that modularity plays an important role in .... \textbf{talk about it here} \cite{Godwin2015}.

Modularity ($Q^w$) in a weighted network can be calculated by the Louvain method \cite{Blondel2008}:

\begin{equation}
Q^w = \frac{1}{I^w} \sum \limits_{i,j} \left[W_{ij} - \frac{k_i^w k_j^w}{I^w} \right] \delta(m_i, m_j),
\end{equation}

in which $w_{i,j}$ is the weight of the edge between nodes $i$ and $j$, $I^w$ represents sum of all weights in the network, $k_i^w$ stands for the weighted degree of node $i$, $m_i$ is the community where node $i$ is located, and $\delta$ is the Kronecker delta function.

\section{\label{sec:level1} Results }

\subsection{\label{sec:level2} Centrality and Dynamics}

\textbf{100 nw is used here. Might have to use 700 nw for consistency.}

\paragraph{Voltage distribution}

Voltage distribution at a specific time $t$ in the network can be roughly determined by the weighted current flow betweenness centrality. As shown in fig. \ref{fig:v_lam_cent}, voltage and filament state as functions of centrality is plotted.

\begin{itemize}
\item \textbf{Rephrase here.}
\item Two clustered groups (ON and OFF). 
\item Transition in between because of the continuity brought in by tunneling model.
\item Maybe include power consumption here as well.
\end{itemize}

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/v_lam_cent}
	\caption{T=2.9, around pathway formation. crosses are voltages and triangles are filament states.}
	\label{fig:v_lam_cent}
\end{figure}

\paragraph{Current flow}

\textbf{Maybe try power dissipation of nanowire as well.}

The cumulative current flow through nanowires shows are linear relationship versus node current flow betweenness centrality. fig. \ref{fig:i_cent}.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/I_cent}
	\caption{Current flow on a nanowire vs node centrality}
	\label{fig:i_cent}
\end{figure}

\subsection{\label{sec:level2} Centrality and Functionality}

\paragraph{Mean communicability}
Briefly Introduce the idea of communicability.

The communicability matrix ($M$) is generated based on $W$.... Each entry represents .... \textbf{might cite some Comm paper here}.

The row sum of $M$ can somehow interpret how communicable a node is to the rest of the network.

The plot of comm vs node closeness cent shows something .....

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/comm_cent}
	\caption{}
	\label{fig:comm_cent}
\end{figure}

\paragraph{Node Transfer Entropy}
The wire closeness centrality also shows an interesting correlation with transfer entropy. More specifically, the capabilities of taking in and giving out information.

The transfer entropy across an edge ($e_{i,j}$) is calculated by:

\textbf{Have to write these equations in a better manner.}

\begin{equation}
TE_{i,j} = T_{V_i \rightarrow V_j}
\end{equation}

And therefore the average outward TE and inward TE of a node can be calculated by:

\begin{equation}
\langle TEout_i \rangle = \frac{\sum \limits_{i,j, A_{i,j} \neq 0} TEout}{\text{\# of edges connected to i}}
\end{equation}

With 50 repetitions of different source/target pairing (while keeping the graphical distance between them constant), TE shows a close to linear relationship with centrality as well:

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/in_TE}
	\caption{}
	\label{fig:in_te}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/out_TE}
	\caption{}
	\label{fig:out_te}
\end{figure}

\paragraph{Node Active Information Storage}
\textbf{Not sure whether we need it here}.

\subsection{Time-series analysis}

\paragraph{$\Delta G$}

The conductance time-series of the network reflects the activation stage of the network. Specifically, $\Delta G$ can help identify the avalanche behaviors of the network.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/G_dG_t}
	\caption{}
	\label{fig:g_dg_t}
\end{figure}

\paragraph{TE time series}

The transfer entropy across the whole network is calculated in the same way as before. The average is taken over the whole network the time series to obtain the time series.

Plotting TE time-series together with $\Delta G$ in the same figure, the spikes of both curves coincide.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/TE_dG}
	\caption{}
	\label{fig:te_dg}
\end{figure}

Different amplitude of voltage biases are applied to the network. The activation time and TE peak time in these realizations line-up pretty well.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/TE_act_time}
	\caption{}
	\label{fig:te_act_time}
\end{figure}

\paragraph{Modularity time series}

Modularity of the network is calculated throughout the activation. The drop of Modularity coincide with $\Delta G$ as well.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/mod_dG}
	\caption{}
	\label{fig:mod_dg}
\end{figure}

\subsection{Dual task}

Pre-activate the network with Mackey-Glass signal, extract the state from different time-points. Then do a non-linear signal transform on it.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/dual_task}
	\caption{}
	\label{fig:dual_task}
\end{figure}

\section{\label{sec:level1} Discussion}

\section{\label{sec:level1} Conclusion}

\begin{acknowledgments}
We wish to acknowledge the support of the author community in using
REV\TeX{}, offering suggestions and encouragement, testing new versions,
\dots.
\end{acknowledgments}

\appendix

\section{Appendixes}

\section{A little more on appendixes}

% The \nocite command causes all entries in a bibliography to be printed out
% whether or not they are actually referenced in the text. This is appropriate
% for the sample file to show the different styles of references, but authors
% most likely will not want to use it.
\nocite{*}

\bibliography{paper1} \label{paper1}% Produces the bibliography via BibTeX.
\bibliographystyle{apalike}

\end{document}
%
% ****** End of file apssamp.tex ******

### 2020-04-16 paper1.tex
include Guimera plots
Recent works
recent works

@@
 \usepackage{bm}% bold math
+\usepackage{bbold}
 %\usepackage{hyperref}% add hypertext capabilities
@@
 
-\textbf{talk about how to map the original nanowire network on to a graph}.
+\textbf{Talk about how to map the original nanowire network on to a graph. Cite Zdenka here}.
 
@@
 \end{figure}
+
+\subsection{\label{sec:level2} Simulation}
+When connected to external voltage biases, nanowire networks behave like traditional electrical networks.
+Each component in the network obeys Kirchhoff's law.
+Hence the voltage distribution across the network can be obtained by solving \cite{Dorfler2018}:
+
+\begin{equation}
+{\cal L}^\dagger V = I,
+\end{equation}
+
+where $\mathcal{L}^\dagger$ is the expanded graph Laplacian of the network, composed as:
+
+\begin{equation}
+	\cal L^\dagger = 
+	\left[
+	\begin{array}{c|c}
+	\cal L&  C\\ 
+	\hline
+	C^T & \mathbb{0}  
+	\end{array}
+	\right],
+\end{equation}
+
+in which $\cal L$ is the graph Laplacian and $C$ represents the nodes (wires) connected to external electrodes.
+
+\begin{equation}
+{\cal L} = D - W
+\end{equation}
 
@@
 in which $w_{i,j}$ is the weight of the edge between nodes $i$ and $j$, $I^w$ represents sum of all weights in the network, $k_i^w$ stands for the weighted degree of node $i$, $m_i$ is the community where node $i$ is located, and $\delta$ is the Kronecker delta function.
+
+\subsection{\label{sec:level2} Communicability}
+Communicability in a network represents .... \cite{Estrada2008}.
+
+In this work communicability is calculated based on the weighted connections \cite{Crofts2009}.
+A symmetric matrix $M$ is generated to depict the communicability distribution, where $M_{i,j}$ represents the communicability between nodes $i$ and $j$.
+Therefore, $M$ reads:
+\begin{equation}
+M = \exp{(D^{-1/2} W D^{-1/2})}.
+\end{equation}
 
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{figure/G_dG_t}
-	\caption{}
-	\label{fig:g_dg_t}
-\end{figure}
-
 \paragraph{TE time series}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{figure/TE_dG}
-	\caption{}
-	\label{fig:te_dg}
-\end{figure}
-
 Different amplitude of voltage biases are applied to the network. The activation time and TE peak time in these realizations line-up pretty well.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{figure/TE_act_time}
-	\caption{}
-	\label{fig:te_act_time}
-\end{figure}
 
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{figure/time_series}
+	\caption{}
+	\label{fig:time_series}
+\end{figure}
+
 \begin{figure}[h]
 	\centering
-	\includegraphics[width=1\linewidth]{figure/mod_dG}
+	\includegraphics[width=1\linewidth]{figure/time_align}
 	\caption{}
-	\label{fig:mod_dg}
+	\label{fig:time_align}
 \end{figure}
@@
 
+The Guimera \textbf{cite here} plots can be displayed as follow:
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{figure/guimera_combine}
+	\caption{}
+	\label{fig:guimera_combine}
+\end{figure}
+
+\textbf{Have to match the color bars here.}
+
+\newpage
 \section{\label{sec:level1} Discussion}

### 2020-04-17 paper1.tex
recent works

@@
 \begin{equation}
-{\cal L} = D - W
+{\cal L} = D - W.
 \end{equation}
+
+Here $W$ is the weighted adjacency matrix of the network. The weights on edges are determined based on their conductance:
+\begin{equation}
+	W_{ij} = A_{ij}G(i,j).
+\end{equation}
+
+And $D$ is the weighted degree matrix generated from $W$:
+\begin{align}
+	d_i = \sum \limits_{k=1}^{N} W_{i,k},\\
+	D = \textbf{diag}(d_i).
+\end{align}
 
@@
 
+\subsection{\label{sec:level2} Communicability}
+Communicability in a network represents .... \cite{Estrada2008}.
+
+In this work communicability is calculated based on the weighted connections \cite{Crofts2009}.
+A symmetric matrix $M$ is generated to depict the communicability distribution, where $M_{i,j}$ represents the communicability between nodes $i$ and $j$.
+Therefore, $M$ reads:
+\begin{equation}
+M = \exp{(D^{-1/2} W D^{-1/2})}.
+\end{equation}
+
+\subsection{\label{sec:level2} Modularity}
+Modularity is a network metric that ..... \textbf{talk about it here} \cite{Rubinov2009}.
+
+Recent studies in neuro-science demonstrated that modularity plays an important role in .... \textbf{talk about it here} \cite{Godwin2015}.
+
+Modularity ($Q^w$) in a weighted network can be calculated by the Louvain method \cite{Blondel2008}:
+
+% \begin{equation}
+% Q^w = \frac{1}{I^w} \sum \limits_{i,j} \left[W_{ij} - \frac{k_i^w k_j^w}{I^w} \right] \delta(m_i, m_j),
+% \end{equation}
+\begin{equation}
+Q^w = \frac{1}{D} \sum \limits_{i,j} \left[W_{ij} - \frac{d_i d_j}{D} \right] \delta(m_i, m_j),
+\end{equation}
+
+in which $w_{i,j}$ is the weight of the edge between nodes $i$ and $j$, $I^w$ represents sum of all weights in the network, $k_i^w$ stands for the weighted degree of node $i$, $m_i$ is the community where node $i$ is located, and $\delta$ is the Kronecker delta function.
+
 \subsection{\label{sec:level2} Transfer Entropy}
@@
 
-\subsection{\label{sec:level2} Modularity}
-Modularity is a network metric that ..... \textbf{talk about it here} \cite{Rubinov2009}.
-
-Recent studies in neuro-science demonstrated that modularity plays an important role in .... \textbf{talk about it here} \cite{Godwin2015}.
-
-Modularity ($Q^w$) in a weighted network can be calculated by the Louvain method \cite{Blondel2008}:
+The transfer entropy across an edge ($e_{i,j}$) is calculated by:
+\textbf{Have to write these equations in a better manner.}
 
 \begin{equation}
-Q^w = \frac{1}{I^w} \sum \limits_{i,j} \left[W_{ij} - \frac{k_i^w k_j^w}{I^w} \right] \delta(m_i, m_j),
+TE_{i,j} = T_{V_i \rightarrow V_j}
 \end{equation}
 
-in which $w_{i,j}$ is the weight of the edge between nodes $i$ and $j$, $I^w$ represents sum of all weights in the network, $k_i^w$ stands for the weighted degree of node $i$, $m_i$ is the community where node $i$ is located, and $\delta$ is the Kronecker delta function.
+And therefore the average outward TE and inward TE of a node can be calculated by:
 
-\subsection{\label{sec:level2} Communicability}
-Communicability in a network represents .... \cite{Estrada2008}.
-
-In this work communicability is calculated based on the weighted connections \cite{Crofts2009}.
-A symmetric matrix $M$ is generated to depict the communicability distribution, where $M_{i,j}$ represents the communicability between nodes $i$ and $j$.
-Therefore, $M$ reads:
 \begin{equation}
-M = \exp{(D^{-1/2} W D^{-1/2})}.
+\langle TEout_i \rangle = \frac{\sum \limits_{i,j, A_{i,j} \neq 0} TEout}{\text{\# of edges connected to i}}
 \end{equation}
@@
 
+As the network evolves, the edges close to sources and drains will be turned on first.
+A winner-takes-all current path will form, then branches out to the rest of the network.
+Among all sorts of metrics, voltage distribution on nodes $\vec{V_n}$ and on edges $\vec{V_e}$ would be the most important ones as they determine the network's state.
+
 \paragraph{Voltage distribution}
 
-Voltage distribution at a specific time $t$ in the network can be roughly determined by the weighted current flow betweenness centrality.
-As shown in fig.
-\ref{fig:v_lam_cent}, voltage and filament state as functions of centrality is plotted.
+Voltage distribution on edges at a specific time $\vec{V_e}(t)$ shows a clear correlation with edge current flow betweenness centrality.
+Meanwhile, since the filament states $\lambda$ strongly rely on voltage distribution $\vec{V_e}(t)$, a correlation between $\lambda$ and EBC as well.
+As plotted in fig.
+\ref{fig:v_lam_cent}, for $\vec{V_e(t)}$ two linear groups
 
@@
 The wire closeness centrality also shows an interesting correlation with transfer entropy. More specifically, the capabilities of taking in and giving out information.
-
-The transfer entropy across an edge ($e_{i,j}$) is calculated by:
-
-\textbf{Have to write these equations in a better manner.}
-
-\begin{equation}
-TE_{i,j} = T_{V_i \rightarrow V_j}
-\end{equation}
-
-And therefore the average outward TE and inward TE of a node can be calculated by:
-
-\begin{equation}
-\langle TEout_i \rangle = \frac{\sum \limits_{i,j, A_{i,j} \neq 0} TEout}{\text{\# of edges connected to i}}
-\end{equation}
 
@@
 \subsection{Dual task}
+\textbf{Might change to a smaller amplitude. Here modularity peak at $t=10$, too small to capture TE.}
 
@@
 \bibliography{paper1} \label{paper1}% Produces the bibliography via BibTeX.
-\bibliographystyle{apalike}
 

### 2020-04-29 paper1.tex
recent works

@@
 
-\title{Manuscript Title:\\with Forced Linebreak}% Force line breaks with \\
+\title{Spatio-temporal dynamics in nanowire networks}% Force line breaks with \\
 \thanks{A footnote to the article title}%
@@
 c_{CB}(e) = \frac{\sum \limits_{s \neq t \in V}\tau_{st}(e)}{(n-1)(n-2)},
+\label{eq:ebc}
 \end{equation}
@@
 In this work communicability is calculated based on the weighted connections \cite{Crofts2009}.
-A symmetric matrix $M$ is generated to depict the communicability distribution, where $M_{i,j}$ represents the communicability between nodes $i$ and $j$.
+A symmetric matrix $M$ is generated to depict the communicability distribution, where $M_{ij}$ represents the communicability between nodes $i$ and $j$.
 Therefore, $M$ reads:
@@
 M = \exp{(D^{-1/2} W D^{-1/2})}.
+\end{equation}
+
+The communicability of a node can be defined as how communicable the node is to the rest of the network, which will have the expression as:
+
+\begin{equation}
+	m_i = \sum \limits_{k = 1}^N M_{ik}, \qquad k \neq i.
 \end{equation}
@@
 Q^w = \frac{1}{D} \sum \limits_{i,j} \left[W_{ij} - \frac{d_i d_j}{D} \right] \delta(m_i, m_j),
+\label{eq:mod}
 \end{equation}
@@
 
-\textbf{100 nw is used here. Might have to use 700 nw for consistency.}
+As the network evolves, the edges close to sources and drains will be turned on first.
+A winner-takes-all current path will be formed, then branches out to the rest of the network.
+The current paths are more likely to be formed first at the most central positions and then the peripherals.
+At a specific time $t$, current-flow betweenness centrality of edges can be determined by \ref{eq:ebc}.
+The edges with higher centrality are more likely to exhibit higher filament state and voltage.
 
-As the network evolves, the edges close to sources and drains will be turned on first.
-A winner-takes-all current path will form, then branches out to the rest of the network.
-Among all sorts of metrics, voltage distribution on nodes $\vec{V_n}$ and on edges $\vec{V_e}$ would be the most important ones as they determine the network's state.
+Meanwhile, voltage ($\vec{V_e}$) and filament state ($\vec{\lambda}$) are strongly coupled in the network.
+Higher voltage on an edge will lead to faster growth of its filament state.
+In return, higher filament state  means the edge will have a higher conductance (\textbf{refer to equation here}), which increase the chance for the edge to achieve higher voltage.
+
+% Among all sorts of metrics, voltage distribution on nodes $\vec{V_n}$ and on edges $\vec{V_e}$ would be the most interesting ones since the change rate of conductances exhibited by edges are determined by $\vec{V_e}$.
+Meanwhile changes of conductance at edges will lead to a redistribution of voltage across the voltage.
+
+\paragraph{Filament state}
+
+The absolute values of filament states $|\vec{\lambda (t)}|$ as a function of edge current-flow betweenness centrality are plotted on fig.
+\ref{fig:v_lam_cent} with its data points colored by corresponding conductance states.
+The plot shows that edges at more preferable positions will have greater filament growth.
+The color spectrum on the plot also validates the conductance transition of edges based on their filament states.
+These high centrality edges are having significantly higher conductance since their filament states are greater than $0.1$, and thus form the first current path.
 
@@
 
-Voltage distribution on edges at a specific time $\vec{V_e}(t)$ shows a clear correlation with edge current flow betweenness centrality.
-Meanwhile, since the filament states $\lambda$ strongly rely on voltage distribution $\vec{V_e}(t)$, a correlation between $\lambda$ and EBC as well.
-As plotted in fig.
-\ref{fig:v_lam_cent}, for $\vec{V_e(t)}$ two linear groups
-
-\begin{itemize}
-\item \textbf{Rephrase here.}
-\item Two clustered groups (ON and OFF). 
-\item Transition in between because of the continuity brought in by tunneling model.
-\item Maybe include power consumption here as well.
-\end{itemize}
+Voltage distribution on edges $|\vec{V_e(t)}|$ as a function of centrality is also included in fig.
+\ref{fig:v_lam_cent} with the same coloring scheme.
+The data points can be clearly classified into three regimes.
+The two linear regimes at the left and right ends correspond to the OFF and ON edges.
+The transition regime in between therefore represents the edges whose conductance are at some middle values in the tunneling model.
+The plot indicates that within each regime, edges with higher centrality will have higher voltage.
+The ones who are having higher voltages will be turned on first to form a current path.
 
@@
 	\includegraphics[width=1\linewidth]{figure/v_lam_cent}
-	\caption{T=2.9, around pathway formation. crosses are voltages and triangles are filament states.}
+	\caption{Absolute values of voltage and filament as a function of centrality at T = 2.9 s.
+Current path was formed at .
+Current-flow betweenness centrality is calculated by Eq.
+\ref{eq:ebc}.
+The data points are colored based on their corresponding conductance.}
 	\label{fig:v_lam_cent}
@@
 \paragraph{Current flow}
-
-\textbf{Maybe try power dissipation of nanowire as well.}
-
+\textbf{Not sure if we have  to keep this}
 The cumulative current flow through nanowires shows are linear relationship versus node current flow betweenness centrality. fig. \ref{fig:i_cent}.
@@
 
+\newpage
 \subsection{\label{sec:level2} Centrality and Functionality}
@@
 	\includegraphics[width=1\linewidth]{figure/in_TE}
-	\caption{}
+	\caption{\textbf{Might not need color here.
+Node in TE as a function of centrality.
+(Out TE in  supplement)} TE is calculated based on Eq \textbf{equation}.
+Node centrality is calculated based on the current-flow closeness algorithm at $t = 0$.
+Communicability is calculated by Eq \textbf{equation} at $t = 0$ as well.
+50 simulations with different source-drain pairings are done on the same 100 network.
+All the source-drain pairings are controlled to have same graphical distance.
+Identical Mackey-Glass signals are applied to these simulations to activate the network.
+Each data point on the plot represent one node in one simulation.
+A close to linear correlation between TE and centrality can be determined from the plot, which means nodes with higher centralities tend to have richer dynamics for taking in and sending out information.}
 	\label{fig:in_te}
@@
 	\centering
-	\includegraphics[width=1\linewidth]{figure/out_TE}
+	\includegraphics[width=1\linewidth]{figure/TE_cent_act}
 	\caption{}
-	\label{fig:out_te}
+	\label{fig:TE_cent_act}
 \end{figure}
@@
 
-\paragraph{$\Delta G$}
-
-The conductance time-series of the network reflects the activation stage of the network. Specifically, $\Delta G$ can help identify the avalanche behaviors of the network.
-
-\paragraph{TE time series}
-
-The transfer entropy across the whole network is calculated in the same way as before. The average is taken over the whole network the time series to obtain the time series.
-
-Plotting TE time-series together with $\Delta G$ in the same figure, the spikes of both curves coincide.
-
-Different amplitude of voltage biases are applied to the network. The activation time and TE peak time in these realizations line-up pretty well.
-
-\paragraph{Modularity time series}
-
-Modularity of the network is calculated throughout the activation. The drop of Modularity coincide with $\Delta G$ as well.
-
 \begin{figure}
@@
 	\includegraphics[width=1\linewidth]{figure/time_series}
-	\caption{}
+	\caption{\textbf{Time series data for network measures.} The dashed vertical green line represents the 			time of first current path formation.
+			\newline (a) Collective conductance of network as a function of time.
+The collective conductance started increasing when the first edge is turned on.
+The growth will slow down after the first current path is formed.
+			\newline (b) The time derivative of conductance.
+The derivative is calculated using second order accurate central differences on the collective conductance time series data.
+The growth regime of conductance shows a great correspondence of $\Delta G$'s spikes.
+			\newline (c) Transfer entropy as a function of time.
+The transfer entropy time series data here is calculated with the Kraskov estimator and averaged across the network.
+A moving average with window size of 100 is applied to smooth the curve.
+Transfer entropy in the activation period is significantly higher than the rest.
+			\newline (d) Modularity as a function of time.
+The weighted modularity of network is calculated by Louvain method(Eq.
+\ref{eq:mod}) As the network evolves, modularity will first increase as high conductance edges are spread across the network and having their own communities.
+With the formation of the first current path, the modularity will have a significant drop since these isolating communities are connected.
+Then the modularity will keep having such fluctuations with smaller scales as more edges are turned on and forming new current paths.}
 	\label{fig:time_series}
@@
 
+Time series analysis of the network's activation can be even more intriguing.
+As plotted in Fig.
+\ref{fig:time_series}(a), the activation of the network mainly have three regimes - the resting (\textbf{maybe another word} ?ground ?low-conductance) regime, the transition regime and the stable (?equilibrium ?high-conductance) regime.
+Key events of the activation also coincide with each other on time scale.
+
+In the resting regime, the junctions are all OFF.
+Collective conductance of the network remains low.
+Filament states on junctions start to grow based on their voltage.
+Increase of conductance will first take place at junctions with preferred positions.
+Information flow is high when the signal first came in, but in general at a low level in this regime.
+The modularity level stays constant when all junctions are at low-conductance state.
+A peak in modularity will then emerge when certain junctions in the network starts to have higher conductances as they are forming "highlands".
+When more junctions experience conductance increase, modularity starts to drop.
+
+The transition regime starts when the first switches are turned on (\textbf{Here it's the tunneling model so maybe some other wording.
+Like some switches are exhibiting higher conductance}).
+Collective conductance of the network starts to increase significantly as the time derivative will have a spike.
+Modularity of the network reaches the bottom level \textbf{wording here}.
+With more junctions turned ON, the first current path (winner-takes-all) will be formed and the conductance keeps increasing with a lower path.
+Modularity starts to increase again as the nodes on the current path stands out from the rest of the network.
+Information flow will increase to a higher scale (A spike in Gaussian data).
+
+The transition regime ends when most junctions are at high-conductance states (the rest are not reachable with this specific source-drain pairing).
+Collective conductance will be stable at a high level.
+Information flow will decrease to a lower scale similar to the resting regime.
+The modularity will also be stable in this regime.
+
+% \paragraph{$\Delta G$}
+
+% The conductance time-series of the network reflects the activation stage of the network. Specifically, $\Delta G$ can help identify the avalanche behaviors of the network.
+
+% \paragraph{TE time series}
+
+% The transfer entropy across the whole network is calculated in the same way as before. The average is taken over the whole network the time series to obtain the time series.
+
+% Plotting TE time-series together with $\Delta G$ in the same figure, the spikes of both curves coincide.
+
+% Different amplitude of voltage biases are applied to the network. The activation time and TE peak time in these realizations line-up pretty well.
+
+% \paragraph{Modularity time series}
+
+% Modularity of the network is calculated throughout the activation. The drop of Modularity coincide with $\Delta G$ as well.
+
+\newpage
 \begin{figure}[h]
@@
 	\includegraphics[width=1\linewidth]{figure/time_align}
-	\caption{}
+	\caption{\textbf{Key events time as functions of first current path formation time.} 
+			The same 100 network is used for 50 simulations with different source-drain pairings.
+The graphical distances between sources and drains are controlled to be constant.
+Identical Mackey-Glass signal with random amplitudes ranging between 2-5 V are applied to these simulations.
+Simulations with higher amplitudes will form current paths earlier.
+			\newline 
+			X-axis represents the current path formation time in different simulations.
+Y-axis represents the corresponding time for key events to take place in these simulations.
+As shown in this figure, key events such as $\Delta G$ maximum, TE spike (in Gaussian estimation) and modularity drop will happen around the first current path formation time.
+			\newline
+			\textbf{Rephrase here} Thus the network will be optimal for information processing and specific task around the transition phase when the first current path is forming and the network is turning on.
+}
 	\label{fig:time_align}
 \end{figure}
+
+\begin{figure*}[h]
+	\centering
+	\includegraphics[width = 0.8\paperwidth]{figure/time_network_comparison}
+	\caption{\textbf{Network information flow snapshots at different time points.}
+			Snapshots of the network are taken at time points before activation ($t = 0.5s$), when the first current path formation ($t=1.465s$), when the network finishes large scale activation ($t = 2s$) and when the network is stable with high collective conductance ($t = 2.5s$).
+			Nodes are colored with time-averaged TE flow (inTE + outTE) within the last 0.2 second window using the Kraskov estimator.
+Edges are colored by the sum of corresponding transfer entropy in both directions.
+TEs are increasing when the network is being activated and richer dynamics emerge.
+After the network reaches a stable state (t = 2.5 s), the TEs activities decay as well.}
+	\label{fig:network_comparison}
+\end{figure*}
 
@@
 	\centering
-	\includegraphics[width=1\linewidth]{figure/dual_task}
+	\includegraphics[width=1\linewidth]{figure/pre_act_task}
 	\caption{}
-	\label{fig:dual_task}
+	\label{fig:pre_act_task}
 \end{figure}
 
-The Guimera \textbf{cite here} plots can be displayed as follow:
+% The Guimera \textbf{cite here} plots can be displayed as follow:
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{figure/guimera_combine}
-	\caption{}
-	\label{fig:guimera_combine}
-\end{figure}
+% \begin{figure}[h]
+% 	\centering
+% 	\includegraphics[width=1\linewidth]{figure/guimera_combine}
+% 	\caption{}
+% 	\label{fig:guimera_combine}
+% \end{figure}
 
-\textbf{Have to match the color bars here.}
+% \textbf{Have to match the color bars here.}
 

### 2020-05-01 paper1.tex
recent work on results part

@@
 	c_{CC}(v) = \frac{n-1}{\sum \limits_{v \neq w \in V} R(v,w)}.
+	\label{eq:ecc}
 \end{equation}
@@
 	m_i = \sum \limits_{k = 1}^N M_{ik}, \qquad k \neq i.
+	\label{eq:ncomm}
 \end{equation}
@@
 
-\newpage
 \subsection{\label{sec:level2} Centrality and Functionality}
 
-\paragraph{Mean communicability}
-Briefly Introduce the idea of communicability.
+\textbf{WORDING HERE as well.} Intuitively one would think certain nodes in the network will have a more important role for certain functionalities.
+Here analysis of the network's functionality such as communicability and transfer entropy are presented.
 
-The communicability matrix ($M$) is generated based on $W$.... Each entry represents .... \textbf{might cite some Comm paper here}.
+The communicability of nodes at $t$ can be calculated based on eq.
+\ref{eq:ncomm}.
+At an arbitrary time point during the activation (Right after first current path formation here ), when plotted as a function of current-flow closeness centrality on log-log scale, communicability shows as a close to exponential curve, indicating that the nodes at more central positions are more communicable to the rest of the network as this time point.
 
-The row sum of $M$ can somehow interpret how communicable a node is to the rest of the network.
+% \paragraph{Mean communicability}
+% Briefly Introduce the idea of communicability.
 
-The plot of comm vs node closeness cent shows something .....
+% The communicability matrix ($M$) is generated based on $W$.... Each entry represents .... \textbf{might cite some Comm paper here}.
+
+% The row sum of $M$ can somehow interpret how communicable a node is to the rest of the network.
+
+% The plot of comm vs node closeness cent shows something .....
 
@@
 	\includegraphics[width=1\linewidth]{figure/comm_cent}
-	\caption{}
+	\caption{\textbf{Node communicability vs closeness centrality at $t = 2 s$.} Node communicability is calculated by eq.
+\ref{eq:ncomm}.
+Closeness centrality is calculated by eq.
+\ref{eq:ecc}.
+The plot is done on log-log scale.
+As the nodes at more central positions are having much higher communicabilities (and higher conductance).
+And the other nodes follows a close to linear trend.}
 	\label{fig:comm_cent}
@@
 
-\paragraph{Node Transfer Entropy}
-The wire closeness centrality also shows an interesting correlation with transfer entropy. More specifically, the capabilities of taking in and giving out information.
-
-With 50 repetitions of different source/target pairing (while keeping the graphical distance between them constant), TE shows a close to linear relationship with centrality as well:
+The node closeness centrality also shows an interesting correlation with transfer entropy.
+Here in the context of nodes, the in TE and out TE will be the main focus \textbf{Have to write equations to define in and out}.
+With 50 repetitions of different source/target pairing (while keeping the graphical distance between them constant), TE averaged across the whole time-series shows a close to linear relationship with centrality on semilogy scale.
+Centrality here is calculated at $t = 0s$, which reflects the structural properties of the network (as all edges are having same weight at $t = 0s$).
+Nodes at more central positions have the potential to send out and take in more information flows and exhibit richer dynamics.
 
@@
 
+Fig.
+\ref{fig:TE_cent_act} shows the in TE vs C centrality around the time when the first current path forms.
+On a semilogy scale, the high centrality nodes (centrality calculated at $T = 1.5 s$) are having similar TE and high communicabilities.
+These are mainly the nodes connected to the ON edges.
+The low centrality nodes on the other hand indicates that with higher centralities there will be higher TE, which is consistent with our analysis in fig.
+\ref{in_te}.
+
 \begin{figure}[h]
@@
 	\includegraphics[width=1\linewidth]{figure/TE_cent_act}
-	\caption{}
+	\caption{\textbf{inTE vs closeness centrality around activation.} The same activation test is done as fig.
+\ref{fig:in_te}.	TE is averaged in a $0.2s$ window right before the activation (mainly to cancel out the randomness).
+Centrality is measured at the current path formation time.
+The high centrality nodes are the ones connected to ON edges.
+They exhibit high communicabilities and high in/out TEs.
+The nodes in the low centrality group on the other hand indicates that with higher centrality, the nodes will have higher in/out TEs, and thus more capable for information transfer.}
 	\label{fig:TE_cent_act}
@@
 
-\paragraph{Node Active Information Storage}
-\textbf{Not sure whether we need it here}.
+% \paragraph{Node Active Information Storage}
+% \textbf{Not sure whether we need it here}.
 
@@
 
+Snapshots of the network in different phases shown in fig.
+\ref{fig:network_comparison}.
+Nodes are colored with the sum of inTE and outTE averaged in the last $0.2 s$ time window.
+Similarly, edges are colored by the sum of the TE flows in both direction in the last $0.2$ time window.
+(Kraskov estimator is used here.) At $t= 0.5$, the whole network is at rest.
+None of the nodes or edges are having significant information transfer.
+When the first current path is formed at $t = 1.465 s$, some nodes and edges start to have significant information flow, but most flows are happening around the central nodes.
+When $t = 2.0 s$, the information flow is even stronger as more nodes are having high in and out TEs.
+Meanwhile, even nodes at peripheral positions are having significant information flow.
+After the network is in the equilibrium regime for a while ($t = 2.5s$), the information flows decay as the local TE values are significantly lower than the transition regime.
+
+\begin{figure*}[h]
+	\centering
+	\includegraphics[width = 0.8\paperwidth]{figure/time_network_comparison}
+	\caption{\textbf{Network information flow snapshots at different time points.}
+			Snapshots of the network are taken at time points before activation ($t = 0.5s$), when the first current path formation ($t=1.465s$), when the network finishes large scale activation ($t = 2s$) and when the network is stable with high collective conductance ($t = 2.5s$).
+			Nodes are colored with time-averaged TE flow (inTE + outTE) within the last 0.2 second window using the Kraskov estimator.
+Edges are colored by the sum of corresponding transfer entropy in both directions.
+TEs are increasing when the network is being activated and richer dynamics emerge.
+After the network reaches a stable state (t = 2.5 s), the TEs activities decay as well.}
+	\label{fig:network_comparison}
+\end{figure*}
+
+A more thorough validation of the hypothesis is done activating the same network with different source-drain pairings.
+The graphical distance between source and drain in each repetition is controlled to be constant.
+Identical Mackey-Glass signals with arbitrary amplitude (\textbf{maybe another word like strength/ xxx parameter}) between $2-5 V$ are delivered to the network.
+The times when the key events take place are recorded and plotted as fig.
+\ref{fig:time_align}.
+\textbf{Wording HERE} With the current path formation time on the x-axis, times for other key events line up fairly well.
+When the amplitude is larger, the first current path will be formed earlier and similar for other events.
+With amplitude ?
+greater than 3.5V, the key events line up linearly.
+With small amplitudes, the activation takes more time and thus more fluctuations in the dynamics are captured.
+These fluctuations contributes to the outliers in the plot.
+
 % \paragraph{$\Delta G$}
@@
 
-\newpage
 \begin{figure}[h]
@@
 
-\begin{figure*}[h]
-	\centering
-	\includegraphics[width = 0.8\paperwidth]{figure/time_network_comparison}
-	\caption{\textbf{Network information flow snapshots at different time points.}
-			Snapshots of the network are taken at time points before activation ($t = 0.5s$), when the first current path formation ($t=1.465s$), when the network finishes large scale activation ($t = 2s$) and when the network is stable with high collective conductance ($t = 2.5s$).
-			Nodes are colored with time-averaged TE flow (inTE + outTE) within the last 0.2 second window using the Kraskov estimator.
-Edges are colored by the sum of corresponding transfer entropy in both directions.
-TEs are increasing when the network is being activated and richer dynamics emerge.
-After the network reaches a stable state (t = 2.5 s), the TEs activities decay as well.}
-	\label{fig:network_comparison}
-\end{figure*}
-
-\subsection{Dual task}
-\textbf{Might change to a smaller amplitude. Here modularity peak at $t=10$, too small to capture TE.}
+\newpage
+\subsection{Pre activation task}
 
 Pre-activate the network with Mackey-Glass signal, extract the state from different time-points. Then do a non-linear signal transform on it.
+
+Hypothesis: a network at certain modularity level (or initial modularity level) might do a better job in tasks.
+
+A 100 network is activated with Mackey-Glass signal.
+It's modularity time-series is shown in \ref{fig:pre_act_task}.
+As discussed in the result section, the modularity level of the network can somehow reflect the network's current state.
+Then the network's corresponding state (conductance and filament state) at times between $t = 0 - 2 s$ are extracted.
+Non-linear transformation task is then applied to the network starting from those extracted states.
+\textbf{x-axis in plot should be changed.}
+
+Fig. \ref{fig:pre_act_task}(b) shows that ...
+
+A t-test is done ....
 

### 2020-06-04 paper1.tex
recent work on results

@@
 
-\subsection{\label{sec:level2} Transfer Entropy}
+\subsection{\label{sec:level2} Information Dynamics}
 
-Transfer entropy is an effective metric for information transduction ...... \textbf{cite Joe here}.
+Transfer entropy is an effective metric for information dynamics. It explains ..... \textbf{cite Joe here}.
 
@@
 \begin{equation}
-\langle TEout_i \rangle = \frac{\sum \limits_{i,j, A_{i,j} \neq 0} TEout}{\text{\# of edges connected to i}}
+\langle TEout_i \rangle = \frac{\sum \limits_{i,j, A_{i,j} \neq 0} TEout}{\text{\# of edges connected to i}}.
 \end{equation}
 
-\section{\label{sec:level1} Results }
+Meanwhile, active information storage was introduced by Lizier et al. (\textbf{cite Joe)} to measure the effect from the past process $\mathbf X$ to the next observation $X_{n+1}$, which is given by:
 
+\begin{align}
+	A_X = \lim \limits_{k \rightarrow \infty} A_X (k),\\
+	A_X(k) = I(\mathbf X_n^{(k)}; X_{n+1})
+	\label{eq:AIS}
+\end{align}
+
+The active information storage in context of edge voltage distribution is thus calculated by:
+
+.....
+
+\section{\label{sec:level1} Results}
 \subsection{\label{sec:level2} Centrality and Dynamics}
 
-As the network evolves, the edges close to sources and drains will be turned on first.
-A winner-takes-all current path will be formed, then branches out to the rest of the network.
-The current paths are more likely to be formed first at the most central positions and then the peripherals.
-At a specific time $t$, current-flow betweenness centrality of edges can be determined by \ref{eq:ebc}.
+As the network evolves, junction filament states will grow faster at more "central" positions.
+A winner-takes-all current path \textbf{Cite the paper} will form at the most central positions first, then branch out to the rest of the network.
+At a specific time $t$, current-flow betweenness centrality of edges can be determined by Eq.
+\ref{eq:ebc}.
 The edges with higher centrality are more likely to exhibit higher filament state and voltage.
-
-Meanwhile, voltage ($\vec{V_e}$) and filament state ($\vec{\lambda}$) are strongly coupled in the network.
-Higher voltage on an edge will lead to faster growth of its filament state.
-In return, higher filament state  means the edge will have a higher conductance (\textbf{refer to equation here}), which increase the chance for the edge to achieve higher voltage.
+Meanwhile, voltage ($\vec{V_e}$) and filament state ($\vec{\lambda}$) are strongly coupled on the junctions.
+Higher voltage on a junction will lead to faster growth of its filament state.
+In return, higher filament state means the junction will have a higher conductance (\textbf{refer to equation here}), which increase the chance for the edge to achieve higher voltage.
 
@@
 \ref{fig:v_lam_cent} with its data points colored by corresponding conductance states.
-The plot shows that edges at more preferable positions will have greater filament growth.
-The color spectrum on the plot also validates the conductance transition of edges based on their filament states.
-These high centrality edges are having significantly higher conductance since their filament states are greater than $0.1$, and thus form the first current path.
+The plot shows that edges at more preferable positions will have faster filament growth.
+The color spectrum on the plot demonstrates the conductance transition of edges based on their filament states.
+These high centrality edges are having significantly higher conductance \textbf{ (WORDING) since their filament states are greater than the threshold}, and thus form the first current path.
 
@@
 The two linear regimes at the left and right ends correspond to the OFF and ON edges.
-The transition regime in between therefore represents the edges whose conductance are at some middle values in the tunneling model.
+The transition regime in between which represents the edges whose conductance are at some middle values in the tunneling model.
 The plot indicates that within each regime, edges with higher centrality will have higher voltage.
-The ones who are having higher voltages will be turned on first to form a current path.
+The earlier current paths consist of these higher centrality junctions.
 
@@
 	\includegraphics[width=1\linewidth]{figure/v_lam_cent}
-	\caption{Absolute values of voltage and filament as a function of centrality at T = 2.9 s.
-Current path was formed at .
-Current-flow betweenness centrality is calculated by Eq.
-\ref{eq:ebc}.
-The data points are colored based on their corresponding conductance.}
+	\caption{Absolute values of voltage and filament as a function of centrality at T = ??
+s.
+Current path was formed at ??.
+The data points are colored based on the junctions' corresponding conductance.
+\textbf{ASK Zdenka.
+Maybe junction on time will be a more obvious metric.}}
 	\label{fig:v_lam_cent}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{figure/I_cent}
-	\caption{Current flow on a nanowire vs node centrality}
-	\label{fig:i_cent}
-\end{figure}
+% \begin{figure}[h]
+% 	\centering
+% 	\includegraphics[width=1\linewidth]{figure/I_cent}
+% 	\caption{Current flow on a nanowire vs node centrality}
+% 	\label{fig:i_cent}
+% \end{figure}
 
@@
 
-\textbf{WORDING HERE as well.} Intuitively one would think certain nodes in the network will have a more important role for certain functionalities.
+\textbf{NOT sure if we want to keep communicability. Since COMM = $\sum G^k$}
+
+\textbf{WORDING HERE as well.} Intuitively one would think certain nodes in the network will have a more important role for specific functionalities.
 Here analysis of the network's functionality such as communicability and transfer entropy are presented.
+The results suggest that more central wires and junctions have higher importance in information dynamics ...\textbf{MAYBE communicability}.
 
@@
 At an arbitrary time point during the activation (Right after first current path formation here ), when plotted as a function of current-flow closeness centrality on log-log scale, communicability shows as a close to exponential curve, indicating that the nodes at more central positions are more communicable to the rest of the network as this time point.
-
-% \paragraph{Mean communicability}
-% Briefly Introduce the idea of communicability.
-
-% The communicability matrix ($M$) is generated based on $W$.... Each entry represents .... \textbf{might cite some Comm paper here}.
-
-% The row sum of $M$ can somehow interpret how communicable a node is to the rest of the network.
-
-% The plot of comm vs node closeness cent shows something .....
 
@@
 The node closeness centrality also shows an interesting correlation with transfer entropy.
-Here in the context of nodes, the in TE and out TE will be the main focus \textbf{Have to write equations to define in and out}.
-With 50 repetitions of different source/target pairing (while keeping the graphical distance between them constant), TE averaged across the whole time-series shows a close to linear relationship with centrality on semilogy scale.
-Centrality here is calculated at $t = 0s$, which reflects the structural properties of the network (as all edges are having same weight at $t = 0s$).
+For any arbitrary node in the network, the out TE is considered as the average of transfer entropy measured from this node to its neighbors.
+And similarly the in TE is thus the transfer entropy from all the neighbors to this node.
+\textbf{Have to write equations to define in and out}.
+With 50 repetitions of different source/target pairing (while the graphical distance in between is kept constant), TE averaged across the whole time-series shows a close to linear relationship with centrality on a semi-logy scale.
+Centrality here is calculated at $t = 0s$, which reflects the effect from the structural properties of the network (as all edges are having same weight at $t = 0s$).
 Nodes at more central positions have the potential to send out and take in more information flows and exhibit richer dynamics.
+
+Local observations of TE around the formation of winner-takes-all current path ($T = ..$ here) are studied as well. 
+Fig.
+\ref{fig:TE_cent_act} shows the in-TE vs closeness centrality around activation.
+On a semi-logy scale, the high centrality nodes are exhibiting high TE and communicabilities.
+These nodes are connected to junctions that are turned ON already.
+On the other hand, the group at the left of the figure consists of low centrality nodes.
+The transition from low TE to high TE with respect to centrality increase validates the analysis in fig.
+\ref{fig:in_te}.
+
+Furthermore, fig.
+\ref{fig:EC_AIS} suggests that junctions with higher betweenness centralities tend to have lower active information storage and will be turned on relatively earlier.
+This kind of behavior is consistent with our expectation since the junctions at more central locations tend to get higher voltage, thus the filament growth will be faster and the high-conductance state can be reached earlier.
+In addition, these rapid filament growth and conductance increase leads to stronger information dynamics on central junctions.
+Thus their future states are less predictable with their own history, which means the AIS will be lower.
 
@@
 	\caption{\textbf{Might not need color here.
-Node in TE as a function of centrality.
-(Out TE in  supplement)} TE is calculated based on Eq \textbf{equation}.
+Node in-TE as a function of centrality.
+(Out TE in  supplement)} 50 repetitions with different source-drain pairings on the same 100 nw network are plotted.
+Each data point represent one junction in one repetition.
+TE is averaged across the whole time-series.
 Node centrality is calculated based on the current-flow closeness algorithm at $t = 0$.
 Communicability is calculated by Eq \textbf{equation} at $t = 0$ as well.
-50 simulations with different source-drain pairings are done on the same 100 network.
 All the source-drain pairings are controlled to have same graphical distance.
@@
 Each data point on the plot represent one node in one simulation.
-A close to linear correlation between TE and centrality can be determined from the plot, which means nodes with higher centralities tend to have richer dynamics for taking in and sending out information.}
+A close to linear correlation between TE and centrality can be determined from the plot, which means nodes with higher centralities tend to have richer dynamics for taking in and sending out information.
+	\textbf{Intrinsic property of the network that does not have any dynamics. We have structural information here.}}
 	\label{fig:in_te}
 \end{figure}
-
-Fig.
-\ref{fig:TE_cent_act} shows the in TE vs C centrality around the time when the first current path forms.
-On a semilogy scale, the high centrality nodes (centrality calculated at $T = 1.5 s$) are having similar TE and high communicabilities.
-These are mainly the nodes connected to the ON edges.
-The low centrality nodes on the other hand indicates that with higher centralities there will be higher TE, which is consistent with our analysis in fig.
-\ref{in_te}.
 
@@
 	\includegraphics[width=1\linewidth]{figure/TE_cent_act}
-	\caption{\textbf{inTE vs closeness centrality around activation.} The same activation test is done as fig.
+	\caption{\textbf{In-TE vs closeness centrality around activation.} The same activation test is done as fig.
 \ref{fig:in_te}.	TE is averaged in a $0.2s$ window right before the activation (mainly to cancel out the randomness).
-Centrality is measured at the current path formation time.
-The high centrality nodes are the ones connected to ON edges.
-They exhibit high communicabilities and high in/out TEs.
-The nodes in the low centrality group on the other hand indicates that with higher centrality, the nodes will have higher in/out TEs, and thus more capable for information transfer.}
+Centrality is measured at the current path formation time.}
 	\label{fig:TE_cent_act}
@@
 
-% \paragraph{Node Active Information Storage}
-% \textbf{Not sure whether we need it here}.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{figure/EC_AIS.png}
+	\caption{Active information storage of junctions as function of betweenness centrality.}
+	\label{fig:EC_AIS}
+\end{figure}
 
@@
 With the formation of the first current path, the modularity will have a significant drop since these isolating communities are connected.
-Then the modularity will keep having such fluctuations with smaller scales as more edges are turned on and forming new current paths.}
+Then the modularity will keep having such fluctuations with smaller scales as more edges are turned on and forming new current paths.
+			\textbf{Gaussian -linear inter, KSG - nonlinear, sensitive}}
 	\label{fig:time_series}
@@
 Time series analysis of the network's activation can be even more intriguing.
-As plotted in Fig.
-\ref{fig:time_series}(a), the activation of the network mainly have three regimes - the resting (\textbf{maybe another word} ?ground ?low-conductance) regime, the transition regime and the stable (?equilibrium ?high-conductance) regime.
-Key events of the activation also coincide with each other on time scale.
+Fig.
+\ref{fig:time_series}(a) shows the network's collective conductance time-series.
+The activation of the network mainly have three regimes - the resting (\textbf{maybe another word} ?ground ?low-conductance) regime, the transition regime and the stable (?equilibrium ?high-conductance) regime.
+Key events during the activation coincide with each other on time scale.
 
-In the resting regime, the junctions are all OFF.
+In the resting regime, all junctions are OFF.
 Collective conductance of the network remains low.
 Filament states on junctions start to grow based on their voltage.
-Increase of conductance will first take place at junctions with preferred positions.
+Increase of conductance will first take place at junctions with higher centralities.
 Information flow is high when the signal first came in, but in general at a low level in this regime.
-The modularity level stays constant when all junctions are at low-conductance state.
-A peak in modularity will then emerge when certain junctions in the network starts to have higher conductances as they are forming "highlands".
+The modularity level stays constant since all junctions are at low-conductance state.
+A peak in modularity will then emerge when several junctions in the network starts to have higher conductances as they are forming "highlands".
 When more junctions experience conductance increase, modularity starts to drop.
 
-The transition regime starts when the first switches are turned on (\textbf{Here it's the tunneling model so maybe some other wording.
+The transition regime starts when the first junctions is turned on (\textbf{Here it's the tunneling model so maybe some other wording.
 Like some switches are exhibiting higher conductance}).
@@
 Nodes are colored with the sum of inTE and outTE averaged in the last $0.2 s$ time window.
-Similarly, edges are colored by the sum of the TE flows in both direction in the last $0.2$ time window.
-(Kraskov estimator is used here.) At $t= 0.5$, the whole network is at rest.
+Similarly, edges are colored by the sum of the TE flows in both direction in the last $0.2 s$ time window.
+(Kraskov estimator is used here.) At $t= 0.5 s$, the whole network is at rest.
 None of the nodes or edges are having significant information transfer.
@@
 Meanwhile, even nodes at peripheral positions are having significant information flow.
-After the network is in the equilibrium regime for a while ($t = 2.5s$), the information flows decay as the local TE values are significantly lower than the transition regime.
+After the network is in the equilibrium regime for a while ($t = 2.5 s$), the information flows decay as the local TE values are significantly lower than the transition regime.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{figure/time_align}
+	\caption{\textbf{Key events time as functions of first current path formation time.} 
+			The same 100 network is used for 50 simulations with different source-drain pairings.
+The graphical distances between sources and drains are controlled to be constant.
+Identical Mackey-Glass signal with random amplitudes ranging between 2-5 V are applied to these simulations.
+Simulations with higher amplitudes will form current paths earlier.
+			\newline 
+			X-axis represents the current path formation time in different simulations.
+Y-axis represents the corresponding time for key events to take place in these simulations.
+As shown in this figure, key events such as $\Delta G$ maximum, TE spike (in Gaussian estimation) and modularity drop will happen around the first current path formation time.
+			\newline
+			\textbf{Rephrase here} Thus the network will be optimal for information processing and specific task around the transition phase when the first current path is forming and the network is turning on.
+}
+	\label{fig:time_align}
+\end{figure}
 
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{figure/time_align}
-	\caption{\textbf{Key events time as functions of first current path formation time.} 
-			The same 100 network is used for 50 simulations with different source-drain pairings.
-The graphical distances between sources and drains are controlled to be constant.
-Identical Mackey-Glass signal with random amplitudes ranging between 2-5 V are applied to these simulations.
-Simulations with higher amplitudes will form current paths earlier.
-			\newline 
-			X-axis represents the current path formation time in different simulations.
-Y-axis represents the corresponding time for key events to take place in these simulations.
-As shown in this figure, key events such as $\Delta G$ maximum, TE spike (in Gaussian estimation) and modularity drop will happen around the first current path formation time.
-			\newline
-			\textbf{Rephrase here} Thus the network will be optimal for information processing and specific task around the transition phase when the first current path is forming and the network is turning on.
-}
-	\label{fig:time_align}
-\end{figure}
-
-\newpage
 \subsection{Pre activation task}
 
-Pre-activate the network with Mackey-Glass signal, extract the state from different time-points. Then do a non-linear signal transform on it.
+\begin{figure*}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{figure/benchmark.png}
+	\caption{\textbf{Benchmarks of the network with different initial states.} The network's voltage distribution and junction filament states are extracted every 10 time-step during the activation with a Mackey-Glass signal input.
+Memory capacity/ non-linear transformation tests are then performed accordingly initiating from those pre-activated states.
+\\
+	(a) Memory capacity result with respect to different initial states.\\
+	(b) Non-linear transformation performance with respect to different initial states.\\
+	(c) Average active information storage of memory capacity tests.\\
+	(d) Average transfer entropy of non-linear transformation tests.} 
+	\label{fig:benchmark}
+\end{figure*}
 
-Hypothesis: a network at certain modularity level (or initial modularity level) might do a better job in tasks.
+\textbf{Why we care about different initial states?}
 
-A 100 network is activated with Mackey-Glass signal.
-It's modularity time-series is shown in \ref{fig:pre_act_task}.
-As discussed in the result section, the modularity level of the network can somehow reflect the network's current state.
-Then the network's corresponding state (conductance and filament state) at times between $t = 0 - 2 s$ are extracted.
-Non-linear transformation task is then applied to the network starting from those extracted states.
-\textbf{x-axis in plot should be changed.}
+The same 100-nw network is activated with Mackey-Glass signal.
+The states of the network at different stages during the activation process are extracted and employed as initial states for benchmarks tasks.
+Memory capacity and non-linear transformation are used to test the network's performance at different activation levels (details in method part).
 
-Fig. \ref{fig:pre_act_task}(b) shows that ...
+Fig.
+\ref{fig:benchmark} (a) shows the memory capacity of the network with respect to different initial states.
+The tests with pre-activation between 1 to 2 seconds are showing significantly better performance compared to the rest.
+The average active information storages corresponding to these tests are shown in fig.
+\ref{fig:benchmark} (c).
+The states with better performance are exhibiting higher active information storage during the tests.
+Since memory capacity of the network is indicating its capability of short term memory, higher MC coincide with higher AIS is not surprising.
 
-A t-test is done ....
+Meanwhile, fig.
+\ref{fig:benchmark} (b) shows the non-linear transformation performance with different pre-activated states.
+Similar to the results in MC tests, the states with 1 to 2 seconds of pre-activation perform better than others.
+However, with roughly around 1.5 seconds of pre-activation, the performance experience a notable drop, which could be caused by the formation of the first current path.
+As the degree of freedom of voltage distribution is low when the first current path is forming.
+The averaged transfer entropy in non-linear transformation tests is shown in fig.
+\ref{fig:benchmark} (d).
+The better performing states show correspondence with higher averaged transfer entropy.
+Non-linear transformation test requires certainly level of degree of freedom to achieve relatively good performance.
+According to \textbf{TE equation}, those higher TE tests are exhibiting stronger information dynamics, which is mainly caused by the complexity and uncertainty of voltage distribution.
+Thus better NLT performance can be explained by higher transfer entropy values in those tests.
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{figure/pre_act_task}
-	\caption{}
-	\label{fig:pre_act_task}
-\end{figure}
-
-% The Guimera \textbf{cite here} plots can be displayed as follow:
-
-% \begin{figure}[h]
-% 	\centering
-% 	\includegraphics[width=1\linewidth]{figure/guimera_combine}
-% 	\caption{}
-% 	\label{fig:guimera_combine}
-% \end{figure}
-
-% \textbf{Have to match the color bars here.}
-
-\newpage
 \section{\label{sec:level1} Discussion}

### 2020-06-05 paper1.tex
recent work

@@
 %prstper,
-%floatfix,
+floatfix,
 ]{revtex4-2}
@@
 Each component in the network obeys Kirchhoff's law.
-Hence the voltage distribution across the network can be obtained by solving \cite{Dorfler2018}:
+Hence the voltage distribution across the network can be obtained by solving (\cite{Dorfler2018}):
 
@@
 \begin{equation}
-	W_{ij} = A_{ij}G(i,j).
+	\mathbf W_{ij} = \mathbf A_{ij} G(i,j).
 \end{equation}
@@
 \begin{align}
-	d_i = \sum \limits_{k=1}^{N} W_{i,k},\\
-	D = \textbf{diag}(d_i).
+	d_i = \sum \limits_{k=1}^{N} \mathbf W_{i,k},\\
+	\mathbf D = \textbf{diag}(d_i).
 \end{align}
@@
 In this work communicability is calculated based on the weighted connections \cite{Crofts2009}.
-A symmetric matrix $M$ is generated to depict the communicability distribution, where $M_{ij}$ represents the communicability between nodes $i$ and $j$.
-Therefore, $M$ reads:
+A symmetric matrix $\mathbf M$ is generated to depict the communicability distribution, where $\mathbf M_{ij}$ represents the communicability between nodes $i$ and $j$.
+Therefore, $\mathbf M$ reads:
 \begin{equation}
-M = \exp{(D^{-1/2} W D^{-1/2})}.
+\mathbf M = \exp{(\mathbf D^{-1/2} \mathbf W \mathbf D^{-1/2})}.
 \end{equation}
@@
 \begin{equation}
-	m_i = \sum \limits_{k = 1}^N M_{ik}, \qquad k \neq i.
+	m_i = \sum \limits_{k = 1}^N \mathbf M_{ik}, \qquad k \neq i.
 	\label{eq:ncomm}
@@
 
-Modularity ($Q^w$) in a weighted network can be calculated by the Louvain method \cite{Blondel2008}:
+Modularity ($\mathbf Q^w$) in a weighted network can be calculated by the Louvain method \cite{Blondel2008}:
 
@@
 \begin{equation}
-Q^w = \frac{1}{D} \sum \limits_{i,j} \left[W_{ij} - \frac{d_i d_j}{D} \right] \delta(m_i, m_j),
+\mathbf Q^w = \frac{1}{\mathbf D} \sum \limits_{i,j} \left[\mathbf W_{ij} - \frac{d_i d_j}{\mathbf D} \right] \delta(m_i, m_j),
 \label{eq:mod}
@@
 
+\subsection{Benchmark}
+
+Regular reservoir computing realizations are typically initialized with homogeneous or randomly generated states.
+The system then evolves based on specific tasks.
+\textbf{WHY we want different initial states?}
+
+A nanowire network enters different stages during its activation.
+Its states at different stages typically have different voltage distribution, unevenly grew filament states and therefore diverse conductance levels.
+In this section the network's states at different activation stages are extracted and used as initial states for benchmarking.
+Starting from these pre-activated states, memory capacity of the network is measured to estimate the network's ability of reconstructing its short-term memory \textbf{Cite Jaeger}.
+Non-linear transformation is used to test the network's learning ability \textbf{Cite Kevin}.
+
+A randomly generated time series from uniform distribution in the interval $[-2,2]$ is used as the input signal for memory capacity test.
+A linear combination of the network's state at $t$ (node voltage) is applied to reconstruct the previous input at $t - k$.
+$k = 1 ...
+100$ are used to investigate different delayed intervals.
+The $k-$delay memory capacity is defined as:
+\begin{equation}
+	\text{MC}_k = \dfrac{\text{cov}^2(\mathbf u_{t-k}, \mathbf o_t)}{\sigma^2 (\mathbf u_{t-k}) \sigma^2 (\mathbf o_t)}.
+\end{equation}
+The generic memory capacity for the network can thus be calculated as:
+\begin{equation}
+	\text{MC} = \sum \limits_{k=1}^\infty \text{MC}_k.
+\end{equation}
+
+The non-linear transformation task makes use of sinusoidal wave as the input signal and try to transfer the signal to other periodic signals in the shape of square or sawtooth.
+Similar to memory capacity test, linear combinations of the network's states are done to fit the target signal.
+The accuracy is calculated by $1 - \text{RNMSE}$:
+\begin{equation}
+	\text{RNMSE} = \sqrt{\dfrac{\sum (\mathbf Y - \mathbf O)^2}{\sum \mathbf O^2}}.
+\end{equation}
+\clearpage
+
+\textbf{General questions about result part}
+
+\begin{itemize}
+	\item Do we need the current flux vs node centrality? (basically a straight line)
+	\item Do we need communicability? Since COMM = $\sum G^k$ in my definition.
+	\item  For the coloring of TE scatter, ON time might be a more straight forward scheme, e.g. the color-way in AIS vs centrality plot.
+	\item How to name different regimes of activation and what will be the time points to distinguish them.
+	\item What will be the best incentive for different initial states in benchmarking.
+(As far as I know, most of the reservoir computing realizations are based on homogeneous or randomly generated initial states.
+This pre-activated way might be a good alternative.)
+	\item The word usage of node-edge and wire-junction.
+(In the context of graph/network, seems like node and edge are more understandable.
+But when talking about ON/OFF and filament states, I feel like junction makes more sense.
+Should we just use one pair of representation in the paper?)
+\end{itemize}
+
+\clearpage
+
 \section{\label{sec:level1} Results}
@@
 As the network evolves, junction filament states will grow faster at more "central" positions.
-A winner-takes-all current path \textbf{Cite the paper} will form at the most central positions first, then branch out to the rest of the network.
-At a specific time $t$, current-flow betweenness centrality of edges can be determined by Eq.
+A winner-takes-all current path \textbf{Cite Dublin paper} will form at the most central positions first, then branch out to the rest of the network.
+At a specific time $t$, current-flow betweenness centrality of junctions can be determined by Eq.
 \ref{eq:ebc}.
-The edges with higher centrality are more likely to exhibit higher filament state and voltage.
+The junctions with higher centrality are more likely to exhibit higher filament state and voltage.
 Meanwhile, voltage ($\vec{V_e}$) and filament state ($\vec{\lambda}$) are strongly coupled on the junctions.
 Higher voltage on a junction will lead to faster growth of its filament state.
-In return, higher filament state means the junction will have a higher conductance (\textbf{refer to equation here}), which increase the chance for the edge to achieve higher voltage.
+In return, higher filament state means the junction will have a higher conductance (\textbf{refer to equation here}), which increase the chance for the junction to achieve higher voltage.
 
@@
 \ref{fig:v_lam_cent} with its data points colored by corresponding conductance states.
-The plot shows that edges at more preferable positions will have faster filament growth.
-The color spectrum on the plot demonstrates the conductance transition of edges based on their filament states.
-These high centrality edges are having significantly higher conductance \textbf{ (WORDING) since their filament states are greater than the threshold}, and thus form the first current path.
+The plot shows that junctions at more preferable positions will have faster filament growth.
+The color spectrum on the plot demonstrates the conductance transition of junctions based on their filament states.
+These high centrality junctions are having significantly higher conductance \textbf{ (WORDING) since their filament states are greater than the threshold}, and thus form the first current path.
 
@@
 
-Voltage distribution on edges $|\vec{V_e(t)}|$ as a function of centrality is also included in fig.
+Voltage distribution on junctions $|\vec{V_e(t)}|$ as a function of centrality is also included in fig.
 \ref{fig:v_lam_cent} with the same coloring scheme.
 The data points can be clearly classified into three regimes.
-The two linear regimes at the left and right ends correspond to the OFF and ON edges.
-The transition regime in between which represents the edges whose conductance are at some middle values in the tunneling model.
-The plot indicates that within each regime, edges with higher centrality will have higher voltage.
+The two linear regimes at the left and right ends correspond to the OFF and ON junctions.
+The transition regime in between which represents the junctions whose conductance are at some middle values in the tunneling model.
+The plot indicates that within each regime, junctions with higher centrality will have higher voltage.
 The earlier current paths consist of these higher centrality junctions.
@@
 \textbf{Not sure if we have  to keep this}
-The cumulative current flow through nanowires shows are linear relationship versus node current flow betweenness centrality. fig. \ref{fig:i_cent}.
+The cumulative current flow through nanowires shows are linear relationship versus node current flow betweenness centrality. 
+% fig. \ref{fig:i_cent}.
 
-% \begin{figure}[h]
-% 	\centering
-% 	\includegraphics[width=1\linewidth]{figure/I_cent}
-% 	\caption{Current flow on a nanowire vs node centrality}
-% 	\label{fig:i_cent}
-% \end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{figure/I_cent}
+	\caption{Current flow on a nanowire vs node centrality}
+	\label{fig:i_cent}
+\end{figure}
 
@@
 And similarly the in TE is thus the transfer entropy from all the neighbors to this node.
-\textbf{Have to write equations to define in and out}.
+\textbf{(Have to write equations to define in and out)}.
 With 50 repetitions of different source/target pairing (while the graphical distance in between is kept constant), TE averaged across the whole time-series shows a close to linear relationship with centrality on a semi-logy scale.
-Centrality here is calculated at $t = 0s$, which reflects the effect from the structural properties of the network (as all edges are having same weight at $t = 0s$).
+Centrality here is calculated at $t = 0s$, which reflects the effect from the structural properties of the network (as all junctions are having same weight at $t = 0s$).
 Nodes at more central positions have the potential to send out and take in more information flows and exhibit richer dynamics.
@@
 	\centering
-	\includegraphics[width=1\linewidth]{figure/time_series}
+	\includegraphics[width=0.95\linewidth]{figure/time_series}
 	\caption{\textbf{Time series data for network measures.} The dashed vertical green line represents the 			time of first current path formation.
 			\newline (a) Collective conductance of network as a function of time.
-The collective conductance started increasing when the first edge is turned on.
+The collective conductance started increasing when the first junction is turned on.
 The growth will slow down after the first current path is formed.
@@
 The weighted modularity of network is calculated by Louvain method(Eq.
-\ref{eq:mod}) As the network evolves, modularity will first increase as high conductance edges are spread across the network and having their own communities.
+\ref{eq:mod}) As the network evolves, modularity will first increase as high conductance junctions are spread across the network and having their own communities.
 With the formation of the first current path, the modularity will have a significant drop since these isolating communities are connected.
-Then the modularity will keep having such fluctuations with smaller scales as more edges are turned on and forming new current paths.
+Then the modularity will keep having such fluctuations with smaller scales as more junctions are turned on and forming new current paths.
 			\textbf{Gaussian -linear inter, KSG - nonlinear, sensitive}}
@@
 Nodes are colored with the sum of inTE and outTE averaged in the last $0.2 s$ time window.
-Similarly, edges are colored by the sum of the TE flows in both direction in the last $0.2 s$ time window.
+Similarly, junctions are colored by the sum of the TE flows in both direction in the last $0.2 s$ time window.
 (Kraskov estimator is used here.) At $t= 0.5 s$, the whole network is at rest.
-None of the nodes or edges are having significant information transfer.
-When the first current path is formed at $t = 1.465 s$, some nodes and edges start to have significant information flow, but most flows are happening around the central nodes.
+None of the nodes or junctions are having significant information transfer.
+When the first current path is formed at $t = 1.465 s$, some nodes and junctions start to have significant information flow, but most flows are happening around the central nodes.
 When $t = 2.0 s$, the information flow is even stronger as more nodes are having high in and out TEs.
@@
 
-\begin{figure}[h]
+\begin{figure}[]
 	\centering
@@
 
-\begin{figure*}[h]
+\begin{figure*}[]
 	\centering
@@
 			Nodes are colored with time-averaged TE flow (inTE + outTE) within the last 0.2 second window using the Kraskov estimator.
-Edges are colored by the sum of corresponding transfer entropy in both directions.
+junctions are colored by the sum of corresponding transfer entropy in both directions.
 TEs are increasing when the network is being activated and richer dynamics emerge.
@@
 
+\clearpage
 \section{\label{sec:level1} Discussion}

### 2020-06-05 paper1.tex
Combined Alon and Zdenka's comments

@@
 
-\title{Spatio-temporal dynamics in nanowire networks}% Force line breaks with \\
+\title{Information dynamics in neuromorphic nanowire networks}% Force line breaks with \\
 \thanks{A footnote to the article title}%
@@
 	\item Do we need the current flux vs node centrality? (basically a straight line)
+	Nah. Just state node current increases linearly with centrality.
 	\item Do we need communicability? Since COMM = $\sum G^k$ in my definition.
+	Probably not - we have more than enough results and I don't think this adds anything.
 	\item  For the coloring of TE scatter, ON time might be a more straight forward scheme, e.g. the color-way in AIS vs centrality plot.
+	Yes, to be consistent and especially if we don't include common. Also, this will combine fig 6 & 7 into one plot, which is better.
 	\item How to name different regimes of activation and what will be the time points to distinguish them.
+	How about: pre-activation, activation and post-activation?
 	\item What will be the best incentive for different initial states in benchmarking.
@@
 This pre-activated way might be a good alternative.)
+	Let's ask Joe - he and Mac & Mike were looking into this with ANNs as there is now some literature on pre-activating ANNs (but not ESNs/RC networks ).
 	\item The word usage of node-edge and wire-junction.
@@
 Should we just use one pair of representation in the paper?)
+	 Yes we should try and be consistent. For this study, we don't need to use filament, but I think we can interchangably use node/wire and edge/junction, and junction state.
 \end{itemize}
@@
 
-As the network evolves, junction filament states will grow faster at more "central" positions.
-A winner-takes-all current path \textbf{Cite Dublin paper} will form at the most central positions first, then branch out to the rest of the network.
+As the network is being activated, junction filament states will grow faster at more ``central" positions.
+A winner-takes-all current path \textbf{Cite Dublin paper} will form at the most central nodes first, then branch out to the rest of the network.
 At a specific time $t$, current-flow betweenness centrality of junctions can be determined by Eq.
 \ref{eq:ebc}.
-The junctions with higher centrality are more likely to exhibit higher filament state and voltage.
-Meanwhile, voltage ($\vec{V_e}$) and filament state ($\vec{\lambda}$) are strongly coupled on the junctions.
-Higher voltage on a junction will lead to faster growth of its filament state.
-In return, higher filament state means the junction will have a higher conductance (\textbf{refer to equation here}), which increase the chance for the junction to achieve higher voltage.
+Junctions with higher centrality are more likely to exhibit higher filament state and voltage.
+Voltage ($\vec{V_e}$) and filament state ($\vec{\lambda}$) are strongly coupled on the junctions; higher voltage on a junction will lead to faster growth of its filament state.
+In return, a higher filament state means the junction will have a higher conductance (\textbf{refer to equation here}), and an increased chance to reach higher voltage.
 
@@
 The absolute values of filament states $|\vec{\lambda (t)}|$ as a function of edge current-flow betweenness centrality are plotted on fig.
-\ref{fig:v_lam_cent} with its data points colored by corresponding conductance states.
-The plot shows that junctions at more preferable positions will have faster filament growth.
-The color spectrum on the plot demonstrates the conductance transition of junctions based on their filament states.
-These high centrality junctions are having significantly higher conductance \textbf{ (WORDING) since their filament states are greater than the threshold}, and thus form the first current path.
+\ref{fig:v_lam_cent}, colored by corresponding conductance.
+The plot shows that junctions at more central positions will have faster filament growth.
+**  \textbf{[Alon - this is repeating]} The color spectrum on the plot demonstrates the conductance transition of junctions based on their filament states.
+High centrality junctions have significantly higher conductance since their filament states are greater than the threshold [ \textbf{Alon - do you mention threshold earlier?
+talk about threshold or ref]}.
+Consequently, these junctions are preferred during formation of the first current path.
 
@@
 Voltage distribution on junctions $|\vec{V_e(t)}|$ as a function of centrality is also included in fig.
-\ref{fig:v_lam_cent} with the same coloring scheme.
-The data points can be clearly classified into three regimes.
-The two linear regimes at the left and right ends correspond to the OFF and ON junctions.
-The transition regime in between which represents the junctions whose conductance are at some middle values in the tunneling model.
-The plot indicates that within each regime, junctions with higher centrality will have higher voltage.
-The earlier current paths consist of these higher centrality junctions.
+\ref{fig:v_lam_cent}.
+The data points can be clearly classified into three regimes: The two linear regimes at the left and right ends correspond to the OFF and ON junctions.
+The transition regime in the middle consists of the junctions whose conductance are in transient between low and high \textbf{[Alon -  wording here doesn't sound right][Ru - I guess still need some suggestions here]}.
+Within each regime, junctions with higher centrality will have higher voltage.
+Earlier current paths consist of these higher centrality junctions.
 
@@
 \textbf{Not sure if we have  to keep this}
-The cumulative current flow through nanowires shows are linear relationship versus node current flow betweenness centrality. 
+The cumulative current flow through nanowires shows a linear relationship with node current flow betweenness centrality. 
 % fig. \ref{fig:i_cent}.
@@
 
-\textbf{WORDING HERE as well.} Intuitively one would think certain nodes in the network will have a more important role for specific functionalities.
+\textbf{WORDING HERE as well.} Intuitively one would think certain nodes in the network will have a more important role for specific functionalities \textbf{[Alon - based on what intuition?
+maybe citation?][Good question, need to think about it ]}.
 Here analysis of the network's functionality such as communicability and transfer entropy are presented.
@@
 The node closeness centrality also shows an interesting correlation with transfer entropy.
-For any arbitrary node in the network, the out TE is considered as the average of transfer entropy measured from this node to its neighbors.
-And similarly the in TE is thus the transfer entropy from all the neighbors to this node.
+For any node in the network, the out-TE is considered as the average transfer entropy measured from the node to its neighbors.
+Oppositely, the in-TE is defined as the transfer entropy from all neighbors to the node.
 \textbf{(Have to write equations to define in and out)}.
-With 50 repetitions of different source/target pairing (while the graphical distance in between is kept constant), TE averaged across the whole time-series shows a close to linear relationship with centrality on a semi-logy scale.
-Centrality here is calculated at $t = 0s$, which reflects the effect from the structural properties of the network (as all junctions are having same weight at $t = 0s$).
-Nodes at more central positions have the potential to send out and take in more information flows and exhibit richer dynamics.
+With 50 repetitions of different source/target node pairings (while the graphical distance in between is kept constant), TE averaged across the whole time-series shows a close-to-linear relationship with centrality on a semi-logy scale.
+Centrality here is calculated at $t = 0s$, and therefore reflects the influence of the structural properties of the network (as all junctions have equal weights at $t = 0s$).
+Nodes at more central positions have the potential to send out and take in more information and exhibit richer dynamics.
 
-Local observations of TE around the formation of winner-takes-all current path ($T = ..$ here) are studied as well. 
+We also locally observe TE around the formation of winner-takes-all current path ($T = ..$ here). 
 Fig.
 \ref{fig:TE_cent_act} shows the in-TE vs closeness centrality around activation.
-On a semi-logy scale, the high centrality nodes are exhibiting high TE and communicabilities.
-These nodes are connected to junctions that are turned ON already.
-On the other hand, the group at the left of the figure consists of low centrality nodes.
+On a semi-logy scale, the high centrality nodes exhibit high TE and communicability.
+At $T = ..$, these nodes are connected to junctions that are already turned ON.
+On the other hand, the group at the left of the figure consists of low centrality nodes \textbf{[Alon - i feel like a sentence is missing explaining this, and connecting to the next sentence]}.
+Within this regime, nodes with higher centralities are more likely to have larger TE.
 The transition from low TE to high TE with respect to centrality increase validates the analysis in fig.
@@
 Furthermore, fig.
-\ref{fig:EC_AIS} suggests that junctions with higher betweenness centralities tend to have lower active information storage and will be turned on relatively earlier.
-This kind of behavior is consistent with our expectation since the junctions at more central locations tend to get higher voltage, thus the filament growth will be faster and the high-conductance state can be reached earlier.
-In addition, these rapid filament growth and conductance increase leads to stronger information dynamics on central junctions.
-Thus their future states are less predictable with their own history, which means the AIS will be lower.
+\ref{fig:EC_AIS} suggests that junctions with higher betweenness centralities tend to have lower active information storage (AIS) and will be turned on relatively earlier.
+This kind of behavior is consistent with our expectation - junctions at more central locations tend to get higher voltage, meaning filament growth will be faster and a high-conductance state may be reached earlier.
+Rapid filament growth and increase of conductance leads to stronger information dynamics on central junctions.
+Thus their future states are less predictable with their own history, which means the AIS will be lower \textbf{[Alon - this sentence needs to be clarified] cite Joe here}.
 

### 2020-06-05 main.tex
change format to SR

--- 2020-06-05 paper1.tex
@@
-% ****** Start of file apssamp.tex ******
-%
-%   This file is part of the APS files in the REVTeX 4.2 distribution.
-%   Version 4.2a of REVTeX, December 2014
-%
-%   Copyright (c) 2014 The American Physical Society.
-%
-%   See the REVTeX 4 README file for restrictions and more information.
-%
-% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
-% as well as the rest of the prerequisites for REVTeX 4.2
-%
-% See the REVTeX 4 README file
-% It also requires running BibTeX. The commands are as follows:
-%
-%  1)  latex apssamp.tex
-%  2)  bibtex apssamp
-%  3)  latex apssamp.tex
-%  4)  latex apssamp.tex
-%
-\documentclass[%
- reprint,
-%superscriptaddress,
-%groupedaddress,
-%unsortedaddress,
-%runinaddress,
-%frontmatterverbose, 
-%preprint,
-%preprintnumbers,
-%nofootinbib,
-%nobibnotes,
-%bibnotes,
- amsmath,amssymb,
- aps,
-%pra,
-%prb,
-%rmp,
-%prstab,
-%prstper,
-floatfix,
-]{revtex4-2}
+\documentclass[fleqn,10pt,  amsmath,amssymb,aps]{wlscirep}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{hyperref}
+\usepackage{cleveref}
 
-\usepackage{graphicx}% Include figure files
-\usepackage{dcolumn}% Align table columns on decimal point
-\usepackage{bm}% bold math
-\usepackage{bbold}
-%\usepackage{hyperref}% add hypertext capabilities
-%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
-%\linenumbers\relax % Commence numbering lines
+\title{Information dynamics in neuromorphic nanowire networks}
 
-%\usepackage[showframe,%Uncomment any one of the following lines to test 
-%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
-%%text={7in,10in},centering,
-%%margin=1.5in,
-%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
-%%height=10in,a5paper,hmargin={3cm,0.8in},
-%]{geometry}
+\author[1,*]{Alice Author}
+\author[2]{Bob Author}
+\author[1,2,+]{Christine Author}
+\author[2,+]{Derek Author}
+\affil[1]{Affiliation, department, city, postcode, country}
+\affil[2]{Affiliation, department, city, postcode, country}
 
+\affil[*]{corresponding.author@email.example}
+
+\affil[+]{these authors contributed equally to this work}
+
+%\keywords{Keyword1, Keyword2, Keyword3}
+
+\begin{abstract}
+Example Abstract.
+Abstract must not include subheadings or citations.
+Example Abstract.
+Abstract must not include subheadings or citations.
+Example Abstract.
+Abstract must not include subheadings or citations.
+Example Abstract.
+Abstract must not include subheadings or citations.
+Example Abstract.
+Abstract must not include subheadings or citations.
+Example Abstract.
+Abstract must not include subheadings or citations.
+Example Abstract.
+Abstract must not include subheadings or citations.
+Example Abstract.
+Abstract must not include subheadings or citations.
+\end{abstract}
 \begin{document}
 
-\preprint{APS/123-QED}
+\flushbottom
+\maketitle
+% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
+%
+%  Click the title above to edit the author information and abstract
+%
+\thispagestyle{empty}
 
-\title{Information dynamics in neuromorphic nanowire networks}% Force line breaks with \\
-\thanks{A footnote to the article title}%
+\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.
 
-\author{Ann Author}
- \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
-\author{Second Author}%
- \email{Second.Author@institution.edu}
-\affiliation{%
- Authors' institution and/or address\\
- This line break forced with \textbackslash\textbackslash
-}%
+\section*{Introduction}
 
-\collaboration{MUSO Collaboration}%\noaffiliation
+The Introduction section, of referenced text expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.
 
-\author{Charlie Author}
- \homepage{http://www.Second.institution.edu/~Charlie.Author}
-\affiliation{
- Second institution and/or address\\
- This line break forced% with \\
-}%
-\affiliation{
- Third institution, the second for Charlie Author
-}%
-\author{Delta Author}
-\affiliation{%
- Authors' institution and/or address\\
- This line break forced with \textbackslash\textbackslash
-}%
+\clearpage
 
-\collaboration{CLEO Collaboration}%\noaffiliation
+\textbf{General questions about result part}
 
-\date{\today}% It is always \today, today,
-             %  but any date may be explicitly specified
+%\begin{itemize}
+%	\item Do we need the current flux vs node centrality? (basically a straight line)
+%	Nah. Just state node current increases linearly with centrality.
+%	\item Do we need communicability? Since COMM = $\sum G^k$ in my definition.
+%	Probably not - we have more than enough results and I don't think this adds anything.
+%	\item  For the coloring of TE scatter, ON time might be a more straight forward scheme, e.g.
+the color-way in AIS vs centrality plot.
+[Yes, to be consistent and especially if we don't include common.
+Also, this will combine fig 6 & 7 into one plot, which is better.]
+%	\item How to name different regimes of activation and what will be the time points to distinguish them.
+%	How about: pre-activation, activation and post-activation?
+%	\item What will be the best incentive for different initial states in benchmarking.
+(As far as I know, most of the reservoir computing realizations are based on homogeneous or randomly generated initial states.
+This pre-activated way might be a good alternative.)[Let's ask Joe - he and Mac & Mike were looking into this with ANNs as there is now some literature on pre-activating ANNs (but not ESNs/RC networks ).]
+%	\item The word usage of node-edge and wire-junction.
+(In the context of graph/network, seems like node and edge are more understandable.
+But when talking about ON/OFF and filament states, I feel like junction makes more sense.
+Should we just use one pair of representation in the paper?)
+%	 Yes we should try and be consistent. For this study, we don't need to use filament, but I think we can interchangably use node/wire and edge/junction, and junction state.
+%\end{itemize}
 
-\begin{abstract}
-An article usually includes an abstract, a concise summary of the work
-covered at length in the main body of the article. 
-\begin{description}
-\item[Usage]
-Secondary publications and information retrieval purposes.
-\item[Structure]
-You may use the \texttt{description} environment to structure your abstract;
-use the optional argument of the \verb+\item+ command to give the category of each item. 
-\end{description}
-\end{abstract}
+\clearpage
+\section*{Results}
 
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-                              %display desired
-\maketitle
+As the network is being activated, junction filament states will grow faster at more ``central" positions.
+A winner-takes-all current path \textbf{Cite Dublin paper} will form at the most central nodes first, then branch out to the rest of the network.
+At a specific time $t$, current-flow betweenness centrality of junctions can be determined by Eq.
+\ref{eq:ebc}.
+Junctions with higher centrality are more likely to exhibit higher filament state and voltage.
+Voltage ($\vec{V_e}$) and filament state ($\vec{\lambda}$) are strongly coupled on the junctions; higher voltage on a junction will lead to faster growth of its filament state.
+In return, a higher filament state means the junction will have a higher conductance (\textbf{refer to equation here}), and an increased chance to reach higher voltage.
 
-%\tableofcontents
+% Among all sorts of metrics, voltage distribution on nodes $\vec{V_n}$ and on edges $\vec{V_e}$ would be the most interesting ones since the change rate of conductances exhibited by edges are determined by $\vec{V_e}$.
+Meanwhile changes of conductance at edges will lead to a redistribution of voltage across the voltage.
 
-\section{\label{sec:level1}  Introduction}
-\section{\label{sec:level1} Method}
+\paragraph{Filament state}
+
+The absolute values of filament states $|\vec{\lambda (t)}|$ as a function of edge current-flow betweenness centrality are plotted on fig.
+\ref{fig:v_lam_cent}, colored by corresponding conductance.
+The plot shows that junctions at more central positions will have faster filament growth.
+**  \textbf{[Alon - this is repeating]} The color spectrum on the plot demonstrates the conductance transition of junctions based on their filament states.
+High centrality junctions have significantly higher conductance since their filament states are greater than the threshold [ \textbf{Alon - do you mention threshold earlier?
+talk about threshold or ref]}.
+Consequently, these junctions are preferred during formation of the first current path.
+
+\paragraph{Voltage distribution}
+
+Voltage distribution on junctions $|\vec{V_e(t)}|$ as a function of centrality is also included in fig.
+\ref{fig:v_lam_cent}.
+The data points can be clearly classified into three regimes: The two linear regimes at the left and right ends correspond to the OFF and ON junctions.
+The transition regime in the middle consists of the junctions whose conductance are in transient between low and high \textbf{[Alon -  wording here doesn't sound right][Ru - I guess still need some suggestions here]}.
+Within each regime, junctions with higher centrality will have higher voltage.
+Earlier current paths consist of these higher centrality junctions.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\linewidth]{figure/v_lam_cent}
+	\caption{Absolute values of voltage and filament as a function of centrality at T = ??
+s.
+Current path was formed at ??.
+The data points are colored based on the junctions' corresponding conductance.
+\textbf{ASK Zdenka.
+Maybe junction on time will be a more obvious metric.}}
+	\label{fig:v_lam_cent}
+\end{figure}
+
+\paragraph{Current flow}
+\textbf{Not sure if we have  to keep this}
+The cumulative current flow through nanowires shows a linear relationship with node current flow betweenness centrality. 
+% fig. \ref{fig:i_cent}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\linewidth]{figure/I_cent}
+	\caption{Current flow on a nanowire vs node centrality}
+	\label{fig:i_cent}
+\end{figure}
+
+\subsection{\label{sec:level2} Centrality and Functionality}
+
+\textbf{NOT sure if we want to keep communicability. Since COMM = $\sum G^k$}
+
+\textbf{WORDING HERE as well.} Intuitively one would think certain nodes in the network will have a more important role for specific functionalities \textbf{[Alon - based on what intuition?
+maybe citation?][Good question, need to think about it ]}.
+Here analysis of the network's functionality such as communicability and transfer entropy are presented.
+The results suggest that more central wires and junctions have higher importance in information dynamics ...\textbf{MAYBE communicability}.
+
+The communicability of nodes at $t$ can be calculated based on eq.
+\ref{eq:ncomm}.
+At an arbitrary time point during the activation (Right after first current path formation here ), when plotted as a function of current-flow closeness centrality on log-log scale, communicability shows as a close to exponential curve, indicating that the nodes at more central positions are more communicable to the rest of the network as this time point.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\linewidth]{figure/comm_cent}
+	\caption{\textbf{Node communicability vs closeness centrality at $t = 2 s$.} Node communicability is calculated by eq.
+\ref{eq:ncomm}.
+Closeness centrality is calculated by eq.
+\ref{eq:ecc}.
+The plot is done on log-log scale.
+As the nodes at more central positions are having much higher communicabilities (and higher conductance).
+And the other nodes follows a close to linear trend.}
+	\label{fig:comm_cent}
+\end{figure}
+
+The node closeness centrality also shows an interesting correlation with transfer entropy.
+For any node in the network, the out-TE is considered as the average transfer entropy measured from the node to its neighbors.
+Oppositely, the in-TE is defined as the transfer entropy from all neighbors to the node.
+\textbf{(Have to write equations to define in and out)}.
+With 50 repetitions of different source/target node pairings (while the graphical distance in between is kept constant), TE averaged across the whole time-series shows a close-to-linear relationship with centrality on a semi-logy scale.
+Centrality here is calculated at $t = 0s$, and therefore reflects the influence of the structural properties of the network (as all junctions have equal weights at $t = 0s$).
+Nodes at more central positions have the potential to send out and take in more information and exhibit richer dynamics.
+
+We also locally observe TE around the formation of winner-takes-all current path ($T = ..$ here). 
+Fig.
+\ref{fig:TE_cent_act} shows the in-TE vs closeness centrality around activation.
+On a semi-logy scale, the high centrality nodes exhibit high TE and communicability.
+At $T = ..$, these nodes are connected to junctions that are already turned ON.
+On the other hand, the group at the left of the figure consists of low centrality nodes \textbf{[Alon - i feel like a sentence is missing explaining this, and connecting to the next sentence]}.
+Within this regime, nodes with higher centralities are more likely to have larger TE.
+The transition from low TE to high TE with respect to centrality increase validates the analysis in fig.
+\ref{fig:in_te}.
+
+Furthermore, fig.
+\ref{fig:EC_AIS} suggests that junctions with higher betweenness centralities tend to have lower active information storage (AIS) and will be turned on relatively earlier.
+This kind of behavior is consistent with our expectation - junctions at more central locations tend to get higher voltage, meaning filament growth will be faster and a high-conductance state may be reached earlier.
+Rapid filament growth and increase of conductance leads to stronger information dynamics on central junctions.
+Thus their future states are less predictable with their own history, which means the AIS will be lower \textbf{[Alon - this sentence needs to be clarified] cite Joe here}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\linewidth]{figure/in_TE}
+	\caption{\textbf{Might not need color here.
+Node in-TE as a function of centrality.
+(Out TE in  supplement)} 50 repetitions with different source-drain pairings on the same 100 nw network are plotted.
+Each data point represent one junction in one repetition.
+TE is averaged across the whole time-series.
+Node centrality is calculated based on the current-flow closeness algorithm at $t = 0$.
+Communicability is calculated by Eq \textbf{equation} at $t = 0$ as well.
+All the source-drain pairings are controlled to have same graphical distance.
+Identical Mackey-Glass signals are applied to these simulations to activate the network.
+Each data point on the plot represent one node in one simulation.
+A close to linear correlation between TE and centrality can be determined from the plot, which means nodes with higher centralities tend to have richer dynamics for taking in and sending out information.
+	\textbf{Intrinsic property of the network that does not have any dynamics. We have structural information here.}}
+	\label{fig:in_te}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\linewidth]{figure/TE_cent_act}
+	\caption{\textbf{In-TE vs closeness centrality around activation.} The same activation test is done as fig.
+\ref{fig:in_te}.	TE is averaged in a $0.2s$ window right before the activation (mainly to cancel out the randomness).
+Centrality is measured at the current path formation time.}
+	\label{fig:TE_cent_act}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\linewidth]{figure/EC_AIS.png}
+	\caption{Active information storage of junctions as function of betweenness centrality.}
+	\label{fig:EC_AIS}
+\end{figure}
+
+\subsection{Time-series analysis}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\linewidth]{figure/time_series}
+	\caption{\textbf{Time series data for network measures.} The dashed vertical green line represents the 			time of first current path formation.
+			\newline (a) Collective conductance of network as a function of time.
+The collective conductance started increasing when the first junction is turned on.
+The growth will slow down after the first current path is formed.
+			\newline (b) The time derivative of conductance.
+The derivative is calculated using second order accurate central differences on the collective conductance time series data.
+The growth regime of conductance shows a great correspondence of $\Delta G$'s spikes.
+			\newline (c) Transfer entropy as a function of time.
+The transfer entropy time series data here is calculated with the Kraskov estimator and averaged across the network.
+A moving average with window size of 100 is applied to smooth the curve.
+Transfer entropy in the activation period is significantly higher than the rest.
+			\newline (d) Modularity as a function of time.
+The weighted modularity of network is calculated by Louvain method(Eq.
+\ref{eq:mod}) As the network evolves, modularity will first increase as high conductance junctions are spread across the network and having their own communities.
+With the formation of the first current path, the modularity will have a significant drop since these isolating communities are connected.
+Then the modularity will keep having such fluctuations with smaller scales as more junctions are turned on and forming new current paths.
+			\textbf{Gaussian -linear inter, KSG - nonlinear, sensitive}}
+	\label{fig:time_series}
+\end{figure}
+
+Time series analysis of the network's activation can be even more intriguing.
+Fig.
+\ref{fig:time_series}(a) shows the network's collective conductance time-series.
+The activation of the network mainly have three regimes - the resting (\textbf{maybe another word} ?ground ?low-conductance) regime, the transition regime and the stable (?equilibrium ?high-conductance) regime.
+Key events during the activation coincide with each other on time scale.
+
+In the resting regime, all junctions are OFF.
+Collective conductance of the network remains low.
+Filament states on junctions start to grow based on their voltage.
+Increase of conductance will first take place at junctions with higher centralities.
+Information flow is high when the signal first came in, but in general at a low level in this regime.
+The modularity level stays constant since all junctions are at low-conductance state.
+A peak in modularity will then emerge when several junctions in the network starts to have higher conductances as they are forming "highlands".
+When more junctions experience conductance increase, modularity starts to drop.
+
+The transition regime starts when the first junctions is turned on (\textbf{Here it's the tunneling model so maybe some other wording.
+Like some switches are exhibiting higher conductance}).
+Collective conductance of the network starts to increase significantly as the time derivative will have a spike.
+Modularity of the network reaches the bottom level \textbf{wording here}.
+With more junctions turned ON, the first current path (winner-takes-all) will be formed and the conductance keeps increasing with a lower path.
+Modularity starts to increase again as the nodes on the current path stands out from the rest of the network.
+Information flow will increase to a higher scale (A spike in Gaussian data).
+
+The transition regime ends when most junctions are at high-conductance states (the rest are not reachable with this specific source-drain pairing).
+Collective conductance will be stable at a high level.
+Information flow will decrease to a lower scale similar to the resting regime.
+The modularity will also be stable in this regime.
+
+Snapshots of the network in different phases shown in fig.
+\ref{fig:network_comparison}.
+Nodes are colored with the sum of inTE and outTE averaged in the last $0.2 s$ time window.
+Similarly, junctions are colored by the sum of the TE flows in both direction in the last $0.2 s$ time window.
+(Kraskov estimator is used here.) At $t= 0.5 s$, the whole network is at rest.
+None of the nodes or junctions are having significant information transfer.
+When the first current path is formed at $t = 1.465 s$, some nodes and junctions start to have significant information flow, but most flows are happening around the central nodes.
+When $t = 2.0 s$, the information flow is even stronger as more nodes are having high in and out TEs.
+Meanwhile, even nodes at peripheral positions are having significant information flow.
+After the network is in the equilibrium regime for a while ($t = 2.5 s$), the information flows decay as the local TE values are significantly lower than the transition regime.
+
+\begin{figure}[]
+	\centering
+	\includegraphics[width=0.5\linewidth]{figure/time_align}
+	\caption{\textbf{Key events time as functions of first current path formation time.} 
+			The same 100 network is used for 50 simulations with different source-drain pairings.
+The graphical distances between sources and drains are controlled to be constant.
+Identical Mackey-Glass signal with random amplitudes ranging between 2-5 V are applied to these simulations.
+Simulations with higher amplitudes will form current paths earlier.
+			\newline 
+			X-axis represents the current path formation time in different simulations.
+Y-axis represents the corresponding time for key events to take place in these simulations.
+As shown in this figure, key events such as $\Delta G$ maximum, TE spike (in Gaussian estimation) and modularity drop will happen around the first current path formation time.
+			\newline
+			\textbf{Rephrase here} Thus the network will be optimal for information processing and specific task around the transition phase when the first current path is forming and the network is turning on.
+}
+	\label{fig:time_align}
+\end{figure}
+
+\begin{figure*}[]
+	\centering
+	\includegraphics[width = 0.8\paperwidth]{figure/time_network_comparison}
+	\caption{\textbf{Network information flow snapshots at different time points.}
+			Snapshots of the network are taken at time points before activation ($t = 0.5s$), when the first current path formation ($t=1.465s$), when the network finishes large scale activation ($t = 2s$) and when the network is stable with high collective conductance ($t = 2.5s$).
+			Nodes are colored with time-averaged TE flow (inTE + outTE) within the last 0.2 second window using the Kraskov estimator.
+junctions are colored by the sum of corresponding transfer entropy in both directions.
+TEs are increasing when the network is being activated and richer dynamics emerge.
+After the network reaches a stable state (t = 2.5 s), the TEs activities decay as well.}
+	\label{fig:network_comparison}
+\end{figure*}
+
+A more thorough validation of the hypothesis is done activating the same network with different source-drain pairings.
+The graphical distance between source and drain in each repetition is controlled to be constant.
+Identical Mackey-Glass signals with arbitrary amplitude (\textbf{maybe another word like strength/ xxx parameter}) between $2-5 V$ are delivered to the network.
+The times when the key events take place are recorded and plotted as fig.
+\ref{fig:time_align}.
+\textbf{Wording HERE} With the current path formation time on the x-axis, times for other key events line up fairly well.
+When the amplitude is larger, the first current path will be formed earlier and similar for other events.
+With amplitude ?
+greater than 3.5V, the key events line up linearly.
+With small amplitudes, the activation takes more time and thus more fluctuations in the dynamics are captured.
+These fluctuations contributes to the outliers in the plot.
+
+% \paragraph{$\Delta G$}
+
+% The conductance time-series of the network reflects the activation stage of the network. Specifically, $\Delta G$ can help identify the avalanche behaviors of the network.
+
+% \paragraph{TE time series}
+
+% The transfer entropy across the whole network is calculated in the same way as before. The average is taken over the whole network the time series to obtain the time series.
+
+% Plotting TE time-series together with $\Delta G$ in the same figure, the spikes of both curves coincide.
+
+% Different amplitude of voltage biases are applied to the network. The activation time and TE peak time in these realizations line-up pretty well.
+
+% \paragraph{Modularity time series}
+
+% Modularity of the network is calculated throughout the activation. The drop of Modularity coincide with $\Delta G$ as well.
+
+\subsection{Pre activation task}
+
+\begin{figure*}[]
+	\centering
+	\includegraphics[width=1\linewidth]{figure/benchmark.png}
+	\caption{\textbf{Benchmarks of the network with different initial states.} The network's voltage distribution and junction filament states are extracted every 10 time-step during the activation with a Mackey-Glass signal input.
+Memory capacity/ non-linear transformation tests are then performed accordingly initiating from those pre-activated states.
+\\
+	(a) Memory capacity result with respect to different initial states.\\
+	(b) Non-linear transformation performance with respect to different initial states.\\
+	(c) Average active information storage of memory capacity tests.\\
+	(d) Average transfer entropy of non-linear transformation tests.} 
+	\label{fig:benchmark}
+\end{figure*}
+
+\textbf{Why we care about different initial states?}
+
+The same 100-nw network is activated with Mackey-Glass signal.
+The states of the network at different stages during the activation process are extracted and employed as initial states for benchmarks tasks.
+Memory capacity and non-linear transformation are used to test the network's performance at different activation levels (details in method part).
+
+Fig.
+\ref{fig:benchmark} (a) shows the memory capacity of the network with respect to different initial states.
+The tests with pre-activation between 1 to 2 seconds are showing significantly better performance compared to the rest.
+The average active information storages corresponding to these tests are shown in fig.
+\ref{fig:benchmark} (c).
+The states with better performance are exhibiting higher active information storage during the tests.
+Since memory capacity of the network is indicating its capability of short term memory, higher MC coincide with higher AIS is not surprising.
+
+Meanwhile, fig.
+\ref{fig:benchmark} (b) shows the non-linear transformation performance with different pre-activated states.
+Similar to the results in MC tests, the states with 1 to 2 seconds of pre-activation perform better than others.
+However, with roughly around 1.5 seconds of pre-activation, the performance experience a notable drop, which could be caused by the formation of the first current path.
+As the degree of freedom of voltage distribution is low when the first current path is forming.
+The averaged transfer entropy in non-linear transformation tests is shown in fig.
+\ref{fig:benchmark} (d).
+The better performing states show correspondence with higher averaged transfer entropy.
+Non-linear transformation test requires certainly level of degree of freedom to achieve relatively good performance.
+According to \textbf{TE equation}, those higher TE tests are exhibiting stronger information dynamics, which is mainly caused by the complexity and uncertainty of voltage distribution.
+Thus better NLT performance can be explained by higher transfer entropy values in those tests.
+
+\clearpage
+
+\section*{Discussion}
+
+The Discussion should be succinct and must not contain subheadings.
+
+\section*{Methods}
 
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{figure/mpl_plot}
+	\includegraphics[width=0.8\linewidth]{figure/mpl_plot}
 	\caption{}
@@
 \end{equation}
-\clearpage
 
-\textbf{General questions about result part}
+\bibliography{paper1}\label{paper1}
 
-\begin{itemize}
-	\item Do we need the current flux vs node centrality? (basically a straight line)
-	Nah. Just state node current increases linearly with centrality.
-	\item Do we need communicability? Since COMM = $\sum G^k$ in my definition.
-	Probably not - we have more than enough results and I don't think this adds anything.
-	\item  For the coloring of TE scatter, ON time might be a more straight forward scheme, e.g. the color-way in AIS vs centrality plot.
-	Yes, to be consistent and especially if we don't include common. Also, this will combine fig 6 & 7 into one plot, which is better.
-	\item How to name different regimes of activation and what will be the time points to distinguish them.
-	How about: pre-activation, activation and post-activation?
-	\item What will be the best incentive for different initial states in benchmarking.
-(As far as I know, most of the reservoir computing realizations are based on homogeneous or randomly generated initial states.
-This pre-activated way might be a good alternative.)
-	Let's ask Joe - he and Mac & Mike were looking into this with ANNs as there is now some literature on pre-activating ANNs (but not ESNs/RC networks ).
-	\item The word usage of node-edge and wire-junction.
-(In the context of graph/network, seems like node and edge are more understandable.
-But when talking about ON/OFF and filament states, I feel like junction makes more sense.
-Should we just use one pair of representation in the paper?)
-	 Yes we should try and be consistent. For this study, we don't need to use filament, but I think we can interchangably use node/wire and edge/junction, and junction state.
-\end{itemize}
+\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu.
+Use the cite command for an inline citation, e.g.
+\cite{Hao:gidmaps:2014}.
 
-\clearpage
+For data citations of datasets uploaded to e.g.
+\emph{figshare}, please use the \verb|howpublished| option in the bib entry to specify the platform and the link, as in the \verb|Hao:gidmaps:2014| example in the sample bibliography file.
 
-\section{\label{sec:level1} Results}
-\subsection{\label{sec:level2} Centrality and Dynamics}
+\section*{Acknowledgements (not compulsory)}
 
-As the network is being activated, junction filament states will grow faster at more ``central" positions.
-A winner-takes-all current path \textbf{Cite Dublin paper} will form at the most central nodes first, then branch out to the rest of the network.
-At a specific time $t$, current-flow betweenness centrality of junctions can be determined by Eq.
-\ref{eq:ebc}.
-Junctions with higher centrality are more likely to exhibit higher filament state and voltage.
-Voltage ($\vec{V_e}$) and filament state ($\vec{\lambda}$) are strongly coupled on the junctions; higher voltage on a junction will lead to faster growth of its filament state.
-In return, a higher filament state means the junction will have a higher conductance (\textbf{refer to equation here}), and an increased chance to reach higher voltage.
+Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.
 
-% Among all sorts of metrics, voltage distribution on nodes $\vec{V_n}$ and on edges $\vec{V_e}$ would be the most interesting ones since the change rate of conductances exhibited by edges are determined by $\vec{V_e}$.
-Meanwhile changes of conductance at edges will lead to a redistribution of voltage across the voltage.
+\section*{Author contributions statement}
 
-\paragraph{Filament state}
+Must include all authors, identified by initials, for example:
+A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript.
 
-The absolute values of filament states $|\vec{\lambda (t)}|$ as a function of edge current-flow betweenness centrality are plotted on fig.
-\ref{fig:v_lam_cent}, colored by corresponding conductance.
-The plot shows that junctions at more central positions will have faster filament growth.
-**  \textbf{[Alon - this is repeating]} The color spectrum on the plot demonstrates the conductance transition of junctions based on their filament states.
-High centrality junctions have significantly higher conductance since their filament states are greater than the threshold [ \textbf{Alon - do you mention threshold earlier?
-talk about threshold or ref]}.
-Consequently, these junctions are preferred during formation of the first current path.
+\section*{Additional information}
 
-\paragraph{Voltage distribution}
+To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing interests} (mandatory statement).
 
-Voltage distribution on junctions $|\vec{V_e(t)}|$ as a function of centrality is also included in fig.
-\ref{fig:v_lam_cent}.
-The data points can be clearly classified into three regimes: The two linear regimes at the left and right ends correspond to the OFF and ON junctions.
-The transition regime in the middle consists of the junctions whose conductance are in transient between low and high \textbf{[Alon -  wording here doesn't sound right][Ru - I guess still need some suggestions here]}.
-Within each regime, junctions with higher centrality will have higher voltage.
-Earlier current paths consist of these higher centrality junctions.
+The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing interests statement} on behalf of all authors of the paper.
+This statement must be included in the submitted article file.
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{figure/v_lam_cent}
-	\caption{Absolute values of voltage and filament as a function of centrality at T = ??
-s.
-Current path was formed at ??.
-The data points are colored based on the junctions' corresponding conductance.
-\textbf{ASK Zdenka.
-Maybe junction on time will be a more obvious metric.}}
-	\label{fig:v_lam_cent}
-\end{figure}
-
-\paragraph{Current flow}
-\textbf{Not sure if we have  to keep this}
-The cumulative current flow through nanowires shows a linear relationship with node current flow betweenness centrality. 
-% fig. \ref{fig:i_cent}.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{figure/I_cent}
-	\caption{Current flow on a nanowire vs node centrality}
-	\label{fig:i_cent}
-\end{figure}
-
-\subsection{\label{sec:level2} Centrality and Functionality}
-
-\textbf{NOT sure if we want to keep communicability. Since COMM = $\sum G^k$}
-
-\textbf{WORDING HERE as well.} Intuitively one would think certain nodes in the network will have a more important role for specific functionalities \textbf{[Alon - based on what intuition?
-maybe citation?][Good question, need to think about it ]}.
-Here analysis of the network's functionality such as communicability and transfer entropy are presented.
-The results suggest that more central wires and junctions have higher importance in information dynamics ...\textbf{MAYBE communicability}.
-
-The communicability of nodes at $t$ can be calculated based on eq.
-\ref{eq:ncomm}.
-At an arbitrary time point during the activation (Right after first current path formation here ), when plotted as a function of current-flow closeness centrality on log-log scale, communicability shows as a close to exponential curve, indicating that the nodes at more central positions are more communicable to the rest of the network as this time point.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{figure/comm_cent}
-	\caption{\textbf{Node communicability vs closeness centrality at $t = 2 s$.} Node communicability is calculated by eq.
-\ref{eq:ncomm}.
-Closeness centrality is calculated by eq.
-\ref{eq:ecc}.
-The plot is done on log-log scale.
-As the nodes at more central positions are having much higher communicabilities (and higher conductance).
-And the other nodes follows a close to linear trend.}
-	\label{fig:comm_cent}
-\end{figure}
-
-The node closeness centrality also shows an interesting correlation with transfer entropy.
-For any node in the network, the out-TE is considered as the average transfer entropy measured from the node to its neighbors.
-Oppositely, the in-TE is defined as the transfer entropy from all neighbors to the node.
-\textbf{(Have to write equations to define in and out)}.
-With 50 repetitions of different source/target node pairings (while the graphical distance in between is kept constant), TE averaged across the whole time-series shows a close-to-linear relationship with centrality on a semi-logy scale.
-Centrality here is calculated at $t = 0s$, and therefore reflects the influence of the structural properties of the network (as all junctions have equal weights at $t = 0s$).
-Nodes at more central positions have the potential to send out and take in more information and exhibit richer dynamics.
-
-We also locally observe TE around the formation of winner-takes-all current path ($T = ..$ here). 
-Fig.
-\ref{fig:TE_cent_act} shows the in-TE vs closeness centrality around activation.
-On a semi-logy scale, the high centrality nodes exhibit high TE and communicability.
-At $T = ..$, these nodes are connected to junctions that are already turned ON.
-On the other hand, the group at the left of the figure consists of low centrality nodes \textbf{[Alon - i feel like a sentence is missing explaining this, and connecting to the next sentence]}.
-Within this regime, nodes with higher centralities are more likely to have larger TE.
-The transition from low TE to high TE with respect to centrality increase validates the analysis in fig.
-\ref{fig:in_te}.
-
-Furthermore, fig.
-\ref{fig:EC_AIS} suggests that junctions with higher betweenness centralities tend to have lower active information storage (AIS) and will be turned on relatively earlier.
-This kind of behavior is consistent with our expectation - junctions at more central locations tend to get higher voltage, meaning filament growth will be faster and a high-conductance state may be reached earlier.
-Rapid filament growth and increase of conductance leads to stronger information dynamics on central junctions.
-Thus their future states are less predictable with their own history, which means the AIS will be lower \textbf{[Alon - this sentence needs to be clarified] cite Joe here}.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{figure/in_TE}
-	\caption{\textbf{Might not need color here.
-Node in-TE as a function of centrality.
-(Out TE in  supplement)} 50 repetitions with different source-drain pairings on the same 100 nw network are plotted.
-Each data point represent one junction in one repetition.
-TE is averaged across the whole time-series.
-Node centrality is calculated based on the current-flow closeness algorithm at $t = 0$.
-Communicability is calculated by Eq \textbf{equation} at $t = 0$ as well.
-All the source-drain pairings are controlled to have same graphical distance.
-Identical Mackey-Glass signals are applied to these simulations to activate the network.
-Each data point on the plot represent one node in one simulation.
-A close to linear correlation between TE and centrality can be determined from the plot, which means nodes with higher centralities tend to have richer dynamics for taking in and sending out information.
-	\textbf{Intrinsic property of the network that does not have any dynamics. We have structural information here.}}
-	\label{fig:in_te}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{figure/TE_cent_act}
-	\caption{\textbf{In-TE vs closeness centrality around activation.} The same activation test is done as fig.
-\ref{fig:in_te}.	TE is averaged in a $0.2s$ window right before the activation (mainly to cancel out the randomness).
-Centrality is measured at the current path formation time.}
-	\label{fig:TE_cent_act}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{figure/EC_AIS.png}
-	\caption{Active information storage of junctions as function of betweenness centrality.}
-	\label{fig:EC_AIS}
-\end{figure}
-
-\subsection{Time-series analysis}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.95\linewidth]{figure/time_series}
-	\caption{\textbf{Time series data for network measures.} The dashed vertical green line represents the 			time of first current path formation.
-			\newline (a) Collective conductance of network as a function of time.
-The collective conductance started increasing when the first junction is turned on.
-The growth will slow down after the first current path is formed.
-			\newline (b) The time derivative of conductance.
-The derivative is calculated using second order accurate central differences on the collective conductance time series data.
-The growth regime of conductance shows a great correspondence of $\Delta G$'s spikes.
-			\newline (c) Transfer entropy as a function of time.
-The transfer entropy time series data here is calculated with the Kraskov estimator and averaged across the network.
-A moving average with window size of 100 is applied to smooth the curve.
-Transfer entropy in the activation period is significantly higher than the rest.
-			\newline (d) Modularity as a function of time.
-The weighted modularity of network is calculated by Louvain method(Eq.
-\ref{eq:mod}) As the network evolves, modularity will first increase as high conductance junctions are spread across the network and having their own communities.
-With the formation of the first current path, the modularity will have a significant drop since these isolating communities are connected.
-Then the modularity will keep having such fluctuations with smaller scales as more junctions are turned on and forming new current paths.
-			\textbf{Gaussian -linear inter, KSG - nonlinear, sensitive}}
-	\label{fig:time_series}
-\end{figure}
-
-Time series analysis of the network's activation can be even more intriguing.
-Fig.
-\ref{fig:time_series}(a) shows the network's collective conductance time-series.
-The activation of the network mainly have three regimes - the resting (\textbf{maybe another word} ?ground ?low-conductance) regime, the transition regime and the stable (?equilibrium ?high-conductance) regime.
-Key events during the activation coincide with each other on time scale.
-
-In the resting regime, all junctions are OFF.
-Collective conductance of the network remains low.
-Filament states on junctions start to grow based on their voltage.
-Increase of conductance will first take place at junctions with higher centralities.
-Information flow is high when the signal first came in, but in general at a low level in this regime.
-The modularity level stays constant since all junctions are at low-conductance state.
-A peak in modularity will then emerge when several junctions in the network starts to have higher conductances as they are forming "highlands".
-When more junctions experience conductance increase, modularity starts to drop.
-
-The transition regime starts when the first junctions is turned on (\textbf{Here it's the tunneling model so maybe some other wording.
-Like some switches are exhibiting higher conductance}).
-Collective conductance of the network starts to increase significantly as the time derivative will have a spike.
-Modularity of the network reaches the bottom level \textbf{wording here}.
-With more junctions turned ON, the first current path (winner-takes-all) will be formed and the conductance keeps increasing with a lower path.
-Modularity starts to increase again as the nodes on the current path stands out from the rest of the network.
-Information flow will increase to a higher scale (A spike in Gaussian data).
-
-The transition regime ends when most junctions are at high-conductance states (the rest are not reachable with this specific source-drain pairing).
-Collective conductance will be stable at a high level.
-Information flow will decrease to a lower scale similar to the resting regime.
-The modularity will also be stable in this regime.
-
-Snapshots of the network in different phases shown in fig.
-\ref{fig:network_comparison}.
-Nodes are colored with the sum of inTE and outTE averaged in the last $0.2 s$ time window.
-Similarly, junctions are colored by the sum of the TE flows in both direction in the last $0.2 s$ time window.
-(Kraskov estimator is used here.) At $t= 0.5 s$, the whole network is at rest.
-None of the nodes or junctions are having significant information transfer.
-When the first current path is formed at $t = 1.465 s$, some nodes and junctions start to have significant information flow, but most flows are happening around the central nodes.
-When $t = 2.0 s$, the information flow is even stronger as more nodes are having high in and out TEs.
-Meanwhile, even nodes at peripheral positions are having significant information flow.
-After the network is in the equilibrium regime for a while ($t = 2.5 s$), the information flows decay as the local TE values are significantly lower than the transition regime.
-
-\begin{figure}[]
-	\centering
-	\includegraphics[width=1\linewidth]{figure/time_align}
-	\caption{\textbf{Key events time as functions of first current path formation time.} 
-			The same 100 network is used for 50 simulations with different source-drain pairings.
-The graphical distances between sources and drains are controlled to be constant.
-Identical Mackey-Glass signal with random amplitudes ranging between 2-5 V are applied to these simulations.
-Simulations with higher amplitudes will form current paths earlier.
-			\newline 
-			X-axis represents the current path formation time in different simulations.
-Y-axis represents the corresponding time for key events to take place in these simulations.
-As shown in this figure, key events such as $\Delta G$ maximum, TE spike (in Gaussian estimation) and modularity drop will happen around the first current path formation time.
-			\newline
-			\textbf{Rephrase here} Thus the network will be optimal for information processing and specific task around the transition phase when the first current path is forming and the network is turning on.
-}
-	\label{fig:time_align}
-\end{figure}
-
-\begin{figure*}[]
-	\centering
-	\includegraphics[width = 0.8\paperwidth]{figure/time_network_comparison}
-	\caption{\textbf{Network information flow snapshots at different time points.}
-			Snapshots of the network are taken at time points before activation ($t = 0.5s$), when the first current path formation ($t=1.465s$), when the network finishes large scale activation ($t = 2s$) and when the network is stable with high collective conductance ($t = 2.5s$).
-			Nodes are colored with time-averaged TE flow (inTE + outTE) within the last 0.2 second window using the Kraskov estimator.
-junctions are colored by the sum of corresponding transfer entropy in both directions.
-TEs are increasing when the network is being activated and richer dynamics emerge.
-After the network reaches a stable state (t = 2.5 s), the TEs activities decay as well.}
-	\label{fig:network_comparison}
-\end{figure*}
-
-A more thorough validation of the hypothesis is done activating the same network with different source-drain pairings.
-The graphical distance between source and drain in each repetition is controlled to be constant.
-Identical Mackey-Glass signals with arbitrary amplitude (\textbf{maybe another word like strength/ xxx parameter}) between $2-5 V$ are delivered to the network.
-The times when the key events take place are recorded and plotted as fig.
-\ref{fig:time_align}.
-\textbf{Wording HERE} With the current path formation time on the x-axis, times for other key events line up fairly well.
-When the amplitude is larger, the first current path will be formed earlier and similar for other events.
-With amplitude ?
-greater than 3.5V, the key events line up linearly.
-With small amplitudes, the activation takes more time and thus more fluctuations in the dynamics are captured.
-These fluctuations contributes to the outliers in the plot.
-
-% \paragraph{$\Delta G$}
-
-% The conductance time-series of the network reflects the activation stage of the network. Specifically, $\Delta G$ can help identify the avalanche behaviors of the network.
-
-% \paragraph{TE time series}
-
-% The transfer entropy across the whole network is calculated in the same way as before. The average is taken over the whole network the time series to obtain the time series.
-
-% Plotting TE time-series together with $\Delta G$ in the same figure, the spikes of both curves coincide.
-
-% Different amplitude of voltage biases are applied to the network. The activation time and TE peak time in these realizations line-up pretty well.
-
-% \paragraph{Modularity time series}
-
-% Modularity of the network is calculated throughout the activation. The drop of Modularity coincide with $\Delta G$ as well.
-
-\subsection{Pre activation task}
-
-\begin{figure*}[]
-	\centering
-	\includegraphics[width=1\linewidth]{figure/benchmark.png}
-	\caption{\textbf{Benchmarks of the network with different initial states.} The network's voltage distribution and junction filament states are extracted every 10 time-step during the activation with a Mackey-Glass signal input.
-Memory capacity/ non-linear transformation tests are then performed accordingly initiating from those pre-activated states.
-\\
-	(a) Memory capacity result with respect to different initial states.\\
-	(b) Non-linear transformation performance with respect to different initial states.\\
-	(c) Average active information storage of memory capacity tests.\\
-	(d) Average transfer entropy of non-linear transformation tests.} 
-	\label{fig:benchmark}
-\end{figure*}
-
-\textbf{Why we care about different initial states?}
-
-The same 100-nw network is activated with Mackey-Glass signal.
-The states of the network at different stages during the activation process are extracted and employed as initial states for benchmarks tasks.
-Memory capacity and non-linear transformation are used to test the network's performance at different activation levels (details in method part).
-
-Fig.
-\ref{fig:benchmark} (a) shows the memory capacity of the network with respect to different initial states.
-The tests with pre-activation between 1 to 2 seconds are showing significantly better performance compared to the rest.
-The average active information storages corresponding to these tests are shown in fig.
-\ref{fig:benchmark} (c).
-The states with better performance are exhibiting higher active information storage during the tests.
-Since memory capacity of the network is indicating its capability of short term memory, higher MC coincide with higher AIS is not surprising.
-
-Meanwhile, fig.
-\ref{fig:benchmark} (b) shows the non-linear transformation performance with different pre-activated states.
-Similar to the results in MC tests, the states with 1 to 2 seconds of pre-activation perform better than others.
-However, with roughly around 1.5 seconds of pre-activation, the performance experience a notable drop, which could be caused by the formation of the first current path.
-As the degree of freedom of voltage distribution is low when the first current path is forming.
-The averaged transfer entropy in non-linear transformation tests is shown in fig.
-\ref{fig:benchmark} (d).
-The better performing states show correspondence with higher averaged transfer entropy.
-Non-linear transformation test requires certainly level of degree of freedom to achieve relatively good performance.
-According to \textbf{TE equation}, those higher TE tests are exhibiting stronger information dynamics, which is mainly caused by the complexity and uncertainty of voltage distribution.
-Thus better NLT performance can be explained by higher transfer entropy values in those tests.
-
-\clearpage
-\section{\label{sec:level1} Discussion}
-
-\section{\label{sec:level1} Conclusion}
-
-\begin{acknowledgments}
-We wish to acknowledge the support of the author community in using
-REV\TeX{}, offering suggestions and encouragement, testing new versions,
-\dots.
-\end{acknowledgments}
-
-\appendix
-
-\section{Appendixes}
-
-\section{A little more on appendixes}
-
-% The \nocite command causes all entries in a bibliography to be printed out
-% whether or not they are actually referenced in the text. This is appropriate
-% for the sample file to show the different styles of references, but authors
-% most likely will not want to use it.
-\nocite{*}
-
-\bibliography{paper1} \label{paper1}% Produces the bibliography via BibTeX.
+Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.
 
 \end{document}
-%
-% ****** End of file apssamp.tex ******

### 2020-06-05 main.tex
format fixes

@@
 
-\subsection{\label{sec:level2} Centrality and Functionality}
+\subsection*{Centrality and Functionality}
 
@@
 
-\subsection{Time-series analysis}
+\subsection*{Time-series analysis}
 
@@
 
-\subsection{Pre activation task}
+\subsection*{Pre activation task}
 
@@
 
-\subsection{Graph Generalization}
+\subsection*{Graph Generalization}
 
@@
 
-\subsection{\label{sec:level2} Simulation}
+\subsection*{\label{sec:level2} Simulation}
 When connected to external voltage biases, nanowire networks behave like traditional electrical networks.
@@
 
-\subsection{\label{sec:level2} Centrality}
+\subsection*{Centrality}
 Centrality \textbf{Put some reference here} is an important measure that helps understand the fundamental structures and connectivities of networks.
@@
 
-\subsection{\label{sec:level2} Communicability}
+\subsection*{Communicability}
 Communicability in a network represents .... \cite{Estrada2008}.
@@
 
-\subsection{\label{sec:level2} Modularity}
+\subsection*{Modularity}
 Modularity is a network metric that ..... \textbf{talk about it here} \cite{Rubinov2009}.
@@
 
-\subsection{\label{sec:level2} Information Dynamics}
+\subsection*{Information Dynamics}
 
@@
 
-\subsection{Benchmark}
+\subsection*{Benchmark}
 

### 2020-06-08 main.tex
highlighted Joel's comments

@@
 
-%\begin{itemize}
-%	\item Do we need the current flux vs node centrality? (basically a straight line)
-%	Nah. Just state node current increases linearly with centrality.
-%	\item Do we need communicability? Since COMM = $\sum G^k$ in my definition.
-%	Probably not - we have more than enough results and I don't think this adds anything.
-%	\item  For the coloring of TE scatter, ON time might be a more straight forward scheme, e.g.
+\begin{itemize}
+	\item Do we need the current flux vs node centrality? (basically a straight line) [Nah. Just state node current increases linearly with centrality.]
+	\item Do we need communicability? Since COMM = $\sum G^k$ in my definition.	[Probably not - we have more than enough results and I don't think this adds anything.]
+	\item  For the coloring of TE scatter, ON time might be a more straight forward scheme, e.g.
 the color-way in AIS vs centrality plot.
 [Yes, to be consistent and especially if we don't include common.
-Also, this will combine fig 6 & 7 into one plot, which is better.]
-%	\item How to name different regimes of activation and what will be the time points to distinguish them.
-%	How about: pre-activation, activation and post-activation?
-%	\item What will be the best incentive for different initial states in benchmarking.
+Also, this will combine fig 6 \& 7 into one plot, which is better.]
+	\item How to name different regimes of activation and what will be the time points to distinguish them. [How about: pre-activation, activation and post-activation?]
+	\item What will be the best incentive for different initial states in benchmarking.
 (As far as I know, most of the reservoir computing realizations are based on homogeneous or randomly generated initial states.
-This pre-activated way might be a good alternative.)[Let's ask Joe - he and Mac & Mike were looking into this with ANNs as there is now some literature on pre-activating ANNs (but not ESNs/RC networks ).]
-%	\item The word usage of node-edge and wire-junction.
+This pre-activated way might be a good alternative.)[Let's ask Joe - he and Mac and Mike were looking into this with ANNs as there is now some literature on pre-activating ANNs (but not ESNs/RC networks ).]
+	\item The word usage of node-edge and wire-junction.
 (In the context of graph/network, seems like node and edge are more understandable.
 But when talking about ON/OFF and filament states, I feel like junction makes more sense.
-Should we just use one pair of representation in the paper?)
-%	 Yes we should try and be consistent. For this study, we don't need to use filament, but I think we can interchangably use node/wire and edge/junction, and junction state.
-%\end{itemize}
+Should we just use one pair of representation in the paper?) [Yes we should try and be consistent.
+For this study, we don't need to use filament, but I think we can interchangably use node/wire and edge/junction, and junction state.]
+\end{itemize}
 
@@
 \section*{Results}
+
+\textbf{Include some explanation about the network's activation under DC signal. And the fact most of the analysis are done with snapshots.}
+
+\textbf{Talk about the sim settings and the network being used.}
 
@@
 \ref{eq:ebc}.
-Junctions with higher centrality are more likely to exhibit higher filament state and voltage.
+Junctions with higher centrality are more likely to exhibit higher voltage and filament state.
 Voltage ($\vec{V_e}$) and filament state ($\vec{\lambda}$) are strongly coupled on the junctions; higher voltage on a junction will lead to faster growth of its filament state.
@@
 
-The absolute values of filament states $|\vec{\lambda (t)}|$ as a function of edge current-flow betweenness centrality are plotted on fig.
+The absolute values of filament states $|\vec{\lambda}(t)|$ as a function of edge current-flow betweenness centrality are plotted on Fig.
 \ref{fig:v_lam_cent}, colored by corresponding conductance.
 The plot shows that junctions at more central positions will have faster filament growth.
-**  \textbf{[Alon - this is repeating]} The color spectrum on the plot demonstrates the conductance transition of junctions based on their filament states.
-High centrality junctions have significantly higher conductance since their filament states are greater than the threshold [ \textbf{Alon - do you mention threshold earlier?
+**  \textbf{[Alon - this is repeating]} The color spectrum on the plot demonstrates the conductance transition of junctions based on their filament states.\textbf{JOEL: could refer to this as an increase in tunnelling conductance or transition to ballistic conductance.} High centrality junctions have significantly higher conductance since their filament states are greater than the threshold [ \textbf{Alon - do you mention threshold earlier?
 talk about threshold or ref]}.
@@
 
-Voltage distribution on junctions $|\vec{V_e(t)}|$ as a function of centrality is also included in fig.
+Voltage distribution on junctions $|\vec{V_e}|(t)$ as a function of centrality is also included in fig.
 \ref{fig:v_lam_cent}.
@@
 Here analysis of the network's functionality such as communicability and transfer entropy are presented.
-The results suggest that more central wires and junctions have higher importance in information dynamics ...\textbf{MAYBE communicability}.
+The results suggest that more central wires (\textbf{Be explicit about more central: higher centrality.}) and junctions have higher importance in information dynamics ...\textbf{MAYBE communicability}.
 
@@
 \textbf{(Have to write equations to define in and out)}.
-With 50 repetitions of different source/target node pairings (while the graphical distance in between is kept constant), TE averaged across the whole time-series shows a close-to-linear relationship with centrality on a semi-logy scale.
-Centrality here is calculated at $t = 0s$, and therefore reflects the influence of the structural properties of the network (as all junctions have equal weights at $t = 0s$).
-Nodes at more central positions have the potential to send out and take in more information and exhibit richer dynamics.
+With 50 repetitions of different source/target node pairings (while the graphical distance in between is kept constant), TE averaged across the whole time-series shows a close-to-linear relationship with centrality on a semi-logy scale in Fig.
+\ref{fig:in_te}.
+Centrality here is calculated at $t = 0\,$s, and therefore reflects the influence of the structural properties of the network (as all junctions have equal weights at $t = 0$s).
+Nodes at more central positions have the potential to send out and take in more information and exhibit richer dynamics (\textbf{might have to explain about "richer"}).
 
-We also locally observe TE around the formation of winner-takes-all current path ($T = ..$ here). 
 Fig.
-\ref{fig:TE_cent_act} shows the in-TE vs closeness centrality around activation.
+\ref{fig:TE_cent_act} shows the in-TE vs closeness centrality around the time of formation of winner-takes-all current path ($T = ..$ here).
 On a semi-logy scale, the high centrality nodes exhibit high TE and communicability.
@@
 
+\textbf{Talk about graph metrics, ON/OFF in INTRO}
+
 Furthermore, fig.
@@
 Rapid filament growth and increase of conductance leads to stronger information dynamics on central junctions.
-Thus their future states are less predictable with their own history, which means the AIS will be lower \textbf{[Alon - this sentence needs to be clarified] cite Joe here}.
+\textbf{(Fast voltage distribution change as well.)} Thus their future states are less predictable with their own history, which means the AIS will be lower \textbf{[Alon - this sentence needs to be clarified] cite Joe here}.
 
@@
 Fig.
-\ref{fig:time_series}(a) shows the network's collective conductance time-series.
-The activation of the network mainly have three regimes - the resting (\textbf{maybe another word} ?ground ?low-conductance) regime, the transition regime and the stable (?equilibrium ?high-conductance) regime.
-Key events during the activation coincide with each other on time scale.
+\ref{fig:time_series}(a) shows the network's collective conductance (\textbf{maybe network conductance}) time-series.
+The activation of the network mainly have three regimes - the resting (\textbf{maybe another word} ?ground ?low-conductance) regime, the transition regime and the stable (?equilibrium JOEL ?high-conductance) regime.
+Key events during the activation coincide with each other as a function of time.
 
@@
 Filament states on junctions start to grow based on their voltage.
-Increase of conductance will first take place at junctions with higher centralities.
-Information flow is high when the signal first came in, but in general at a low level in this regime.
+Increase of conductance will first take place at junctions with higher centralities (voltages).
+Information flow is high when the signal first applied to the network, but in general at a low level in this regime.
 The modularity level stays constant since all junctions are at low-conductance state.
-A peak in modularity will then emerge when several junctions in the network starts to have higher conductances as they are forming "highlands".
+A peak in modularity will then emerge when several junctions in the network starts to have higher conductances as they are forming "highlands" (\textbf{need proper explanation here}).
 When more junctions experience conductance increase, modularity starts to drop.
 
-The transition regime starts when the first junctions is turned on (\textbf{Here it's the tunneling model so maybe some other wording.
+(Refer to \ref{fig:time_series}) The transition regime starts when the first junctions is turned on (\textbf{Here it's the tunneling model so maybe some other wording.
 Like some switches are exhibiting higher conductance}).
 Collective conductance of the network starts to increase significantly as the time derivative will have a spike.
-Modularity of the network reaches the bottom level \textbf{wording here}.
+(\textbf{Connect spikes to formation of pathways???
+Have to check.
+Not sure if a clear connection exists.}) Modularity of the network reaches the bottom level \textbf{wording here}.
 With more junctions turned ON, the first current path (winner-takes-all) will be formed and the conductance keeps increasing with a lower path.
@@
 Information flow will increase to a higher scale (A spike in Gaussian data).
+
+\textbf{Show the regimes on figure.}
 
@@
 \ref{fig:network_comparison}.
-Nodes are colored with the sum of inTE and outTE averaged in the last $0.2 s$ time window.
+Nodes are colored with the sum of inTE and outTE averaged in the last $0.2\,$s time window.
 Similarly, junctions are colored by the sum of the TE flows in both direction in the last $0.2 s$ time window.
@@
 The graphical distance between source and drain in each repetition is controlled to be constant.
-Identical Mackey-Glass signals with arbitrary amplitude (\textbf{maybe another word like strength/ xxx parameter}) between $2-5 V$ are delivered to the network.
+Identical Mackey-Glass signals with arbitrary amplitude (\textbf{maybe another word like strength/ xxx parameter}) between $2-5\,$V are delivered to the network.
 The times when the key events take place are recorded and plotted as fig.
@@
 greater than 3.5V, the key events line up linearly.
-With small amplitudes, the activation takes more time and thus more fluctuations in the dynamics are captured.
+With small amplitudes, the activation takes more time and thus more fluctuations in the dynamics (\textbf{fluctuations in dynamics}) are captured.
 These fluctuations contributes to the outliers in the plot.
@@
 
-The same 100-nw network is activated with Mackey-Glass signal.
-The states of the network at different stages during the activation process are extracted and employed as initial states for benchmarks tasks.
+The same 100-nanowire network is activated with Mackey-Glass signal.(\textbf{Ref here}) The states of the network at different stages during the activation process are extracted and employed as initial states for benchmarks tasks.
 Memory capacity and non-linear transformation are used to test the network's performance at different activation levels (details in method part).
@@
 Fig.
-\ref{fig:benchmark} (a) shows the memory capacity of the network with respect to different initial states.
+\ref{fig:benchmark} (a) shows the memory capacity of the network with respect to different initial states (\textbf{explain different initial states}).
 The tests with pre-activation between 1 to 2 seconds are showing significantly better performance compared to the rest.
@@
 However, with roughly around 1.5 seconds of pre-activation, the performance experience a notable drop, which could be caused by the formation of the first current path.
-As the degree of freedom of voltage distribution is low when the first current path is forming.
+As the degree of freedom of voltage distribution is low (\textbf{Need to work on this}) when the first current path is forming.
 The averaged transfer entropy in non-linear transformation tests is shown in fig.

### 2020-06-10 main.tex
combined Zdenka's changes

@@
 	\item Do we need the current flux vs node centrality? (basically a straight line) [Nah. Just state node current increases linearly with centrality.]
-	\item Do we need communicability? Since COMM = $\sum G^k$ in my definition.	[Probably not - we have more than enough results and I don't think this adds anything.]
+	\item Do we need communicability? Since COMM = $\sum G^k$ in my definition.	[Probably not - we have more than enough results and I don't think this adds anything. Can go in SUPP]
 	\item  For the coloring of TE scatter, ON time might be a more straight forward scheme, e.g.
@@
 
-As the network is being activated, junction filament states will grow faster at more ``central" positions.
-A winner-takes-all current path \textbf{Cite Dublin paper} will form at the most central nodes first, then branch out to the rest of the network.
-At a specific time $t$, current-flow betweenness centrality of junctions can be determined by Eq.
+\textbf{ZK: The first para can be a short preamble to briefly introduce the network model (referring to methods for details) and describe the numerical experiments presented below (without yet mentioning the results.
+Return to this after Results section draft is done.}
+
+As the network activates, junctions at more central locations in the network evolve faster.
+A winner-takes-all (WTA) current path \textbf{Cite Dublin paper} form at the most central nodes first, followed by additional current paths branch out to the rest of the network.
+At a specific time $t$, current-flow betweenness centrality of junctions is determined by Eq.
 \ref{eq:ebc}.
-Junctions with higher centrality are more likely to exhibit higher voltage and filament state.
-Voltage ($\vec{V_e}$) and filament state ($\vec{\lambda}$) are strongly coupled on the junctions; higher voltage on a junction will lead to faster growth of its filament state.
-In return, a higher filament state means the junction will have a higher conductance (\textbf{refer to equation here}), and an increased chance to reach higher voltage.
+Junctions with higher centrality are more likely to receive higher voltage.
+Voltage ($\vec{V_e}$) and conductance are strongly coupled on the junctions; higher voltage on a junction leads to faster evolution of its conductantce state.
+In return, a higher conductance state means the junction is more likely to receive a higher voltage (\textbf{refer to equation here}).\textbf{[ZK: I think it's more complex than this due to topology - the voltage distribution changes adaptively in response to junction state changes.]}
 
@@
 
-\paragraph{Filament state}
+\subsection*{Junction centrality and information spread}
 
-The absolute values of filament states $|\vec{\lambda}(t)|$ as a function of edge current-flow betweenness centrality are plotted on Fig.
+\paragraph{Junction state and network information flow.}
+
+% The absolute values of filament states $|\vec{\lambda}(t)|$ as a function of edge current-flow betweenness centrality are plotted on Fig.
 \ref{fig:v_lam_cent}, colored by corresponding conductance.
@@
 
-\paragraph{Voltage distribution}
+%\paragraph{Voltage distribution}
 
-Voltage distribution on junctions $|\vec{V_e}|(t)$ as a function of centrality is also included in fig.
-\ref{fig:v_lam_cent}.
+% Voltage distribution on junctions $|\vec{V_e}|(t)$ as a function of centrality is also included in fig.
+\ref{fig:ebc+nw}.
 The data points can be clearly classified into three regimes: The two linear regimes at the left and right ends correspond to the OFF and ON junctions.
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\linewidth]{figure/v_lam_cent}
-	\caption{Absolute values of voltage and filament as a function of centrality at T = ??
-s.
-Current path was formed at ??.
-The data points are colored based on the junctions' corresponding conductance.
-\textbf{ASK Zdenka.
-Maybe junction on time will be a more obvious metric.}}
-	\label{fig:v_lam_cent}
-\end{figure}
+Voltage distribution on junctions $|\vec{V_e}|(t)$ as a function of centrality at $t = 1.7$s is plotted in Fig.
+\ref{fig:ebc+nw} where the color code represents each junction's corresponding conductance.
+The data points can be clearly classified into three regimes: The two linear regimes at the left and right ends correspond to the OFF and ON junctions.
+The transition regime in the middle consists of the junctions whose conductance are in transient between low and high \textbf{[Alon -  wording here doesn't sound right][Ru - I guess still need some suggestions here]}.
+Within each regime, junctions with higher centrality will have higher voltage.
+Earlier current paths consist of these higher centrality junctions.
 
-\paragraph{Current flow}
-\textbf{Not sure if we have  to keep this}
-The cumulative current flow through nanowires shows a linear relationship with node current flow betweenness centrality. 
-% fig. \ref{fig:i_cent}.
+The right panel of Fig.
+\ref{fig:ebc+nw} shows the corresponding snapshot of the network at $t = 1.7\,$s.
+The WTA pathway formed earlier (at $t = 1.465 \,$s) is represented by orange nodes.
+The edges are colored based on their corresponding conductance in log scale.
+The positions of high-conductance junctions beside the WTA pathway demonstrate the importance of centrality - the junctions at more central positions are turned on earlier.
 
@@
 	\centering
-	\includegraphics[width=0.5\linewidth]{figure/I_cent}
-	\caption{Current flow on a nanowire vs node centrality}
-	\label{fig:i_cent}
+%	\includegraphics[width=0.5\linewidth]{figure/v_lam_cent}
+	\includegraphics[width=0.8\linewidth]{figure/ebc+nw}
+	\caption{Left -- Voltage magnitude and conductance across network junctions as a function of their current betweenness centrality at $t = 1.7\,$s.
+Right -- corresponding snapshot of network graph, showing the first current path (between orange nodes) established earlier, at $t = 1.7\,$s.
+Dashed edges denote junctions still in an "off" (high resistance) state.}
+	\label{fig:ebc+nw}
 \end{figure}
 
-\subsection*{Centrality and Functionality}
+% \paragraph{Current flow}
+% \textbf{Not sure if we have  to keep this}
+% The cumulative current flow through nanowires shows a linear relationship with node current flow betweenness centrality. 
+% % fig. \ref{fig:i_cent}.
 
-\textbf{NOT sure if we want to keep communicability. Since COMM = $\sum G^k$}
+% \begin{figure}[h]
+% 	\centering
+% 	\includegraphics[width=0.5\linewidth]{figure/I_cent}
+% 	\caption{Current flow on a nanowire vs node centrality}
+% 	\label{fig:i_cent}
+% \end{figure}
 
-\textbf{WORDING HERE as well.} Intuitively one would think certain nodes in the network will have a more important role for specific functionalities \textbf{[Alon - based on what intuition?
+% \subsection*{Centrality and Functionality}
+
+% \textbf{NOT sure if we want to keep communicability. Since COMM = $\sum G^k$}
+
+% \textbf{WORDING HERE as well.} Intuitively one would think certain nodes in the network will have a more important role for specific functionalities \textbf{[Alon - based on what intuition?
 maybe citation?][Good question, need to think about it ]}.
@@
 
-The communicability of nodes at $t$ can be calculated based on eq.
+% The communicability of nodes at $t$ can be calculated based on eq.
 \ref{eq:ncomm}.
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\linewidth]{figure/comm_cent}
-	\caption{\textbf{Node communicability vs closeness centrality at $t = 2 s$.} Node communicability is calculated by eq.
+% \begin{figure}[h]
+% 	\centering
+% 	\includegraphics[width=0.5\linewidth]{figure/comm_cent}
+% 	\caption{\textbf{Node communicability vs closeness centrality at $t = 2 s$.} Node communicability is calculated by eq.
 \ref{eq:ncomm}.
@@
 And the other nodes follows a close to linear trend.}
-	\label{fig:comm_cent}
-\end{figure}
+% 	\label{fig:comm_cent}
+% \end{figure}
 
+\paragraph{Transfer entropy -- information exchange.}
 The node closeness centrality also shows an interesting correlation with transfer entropy.
@@
 	\centering
-	\includegraphics[width=0.5\linewidth]{figure/in_TE}
+	\includegraphics[width=0.45\linewidth]{figure/in_TE}
+	\includegraphics[width=0.45\linewidth]{figure/TE_cent_act}
 	\caption{\textbf{Might not need color here.
 Node in-TE as a function of centrality.
-(Out TE in  supplement)} 50 repetitions with different source-drain pairings on the same 100 nw network are plotted.
+(Out TE in  supplement) ZK: I put these together.
+Can you make them the same scale to compare more easily, showing TE and cc increase at activation time.} 50 repetitions with different source-drain pairings on the same 100 nw network are plotted.
 Each data point represent one junction in one repetition.
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\linewidth]{figure/TE_cent_act}
-	\caption{\textbf{In-TE vs closeness centrality around activation.} The same activation test is done as fig.
+% \begin{figure}[h]
+% 	\centering
+% 	\includegraphics[width=0.5\linewidth]{figure/TE_cent_act}
+% 	\caption{\textbf{In-TE vs closeness centrality around activation.} The same activation test is done as fig.
 \ref{fig:in_te}.	TE is averaged in a $0.2s$ window right before the activation (mainly to cancel out the randomness).
 Centrality is measured at the current path formation time.}
-	\label{fig:TE_cent_act}
-\end{figure}
+% 	\label{fig:TE_cent_act}
+% \end{figure}
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\linewidth]{figure/EC_AIS.png}
-	\caption{Active information storage of junctions as function of betweenness centrality.}
-	\label{fig:EC_AIS}
-\end{figure}
+% \begin{figure}[h]
+% 	\centering
+% 	\includegraphics[width=0.5\linewidth]{figure/EC_AIS.png}
+% 	\caption{Active information storage of junctions as function of betweenness centrality.}
+% 	\label{fig:EC_AIS}
+% \end{figure}
 
-\subsection*{Time-series analysis}
+\subsection*{Neuromorphic information dynamics and learning}
 
@@
 
+\paragraph{Network time series.}
 Time series analysis of the network's activation can be even more intriguing.
@@
 
-\subsection*{Pre activation task}
+%\subsection*{Pre activation task}
 
@@
 
+\paragraph{Network pre--activation -- memory capacity and learning}
 \textbf{Why we care about different initial states?} 
+\textbf{[ZK: do you have learning results without pre-activation?]}
 

### 2020-06-10 main.tex
some local changes

--- 2020-06-08 main.tex
@@
 \usepackage{cleveref}
+\usepackage{subcaption}
 
@@
 
-\textbf{Talk about the sim settings and the network being used.}
-
-As the network is being activated, junction filament states will grow faster at more ``central" positions.
-A winner-takes-all current path \textbf{Cite Dublin paper} will form at the most central nodes first, then branch out to the rest of the network.
-At a specific time $t$, current-flow betweenness centrality of junctions can be determined by Eq.
-\ref{eq:ebc}.
-Junctions with higher centrality are more likely to exhibit higher voltage and filament state.
-Voltage ($\vec{V_e}$) and filament state ($\vec{\lambda}$) are strongly coupled on the junctions; higher voltage on a junction will lead to faster growth of its filament state.
-In return, a higher filament state means the junction will have a higher conductance (\textbf{refer to equation here}), and an increased chance to reach higher voltage.
+A 100-nanowire is activated with a Mackey-Glass signal generated by \textbf{reference}.
+With the input of DC signals, a winner-takes-all (WTA) current pathway bridging between the source and drain will emerge in neuromorphic nanowire networks \textbf{Cite Dublin paper}.
+Such WTA pathways are also observed with single polarity Mackey-Glass signals.
+The activation of the network starts with the formation of the WTA pathway and then branch out to the rest of the network.
+In this study the dynamics are investigated with snapshots of the network at different time points.
 
@@
 
-\paragraph{Filament state}
-
-The absolute values of filament states $|\vec{\lambda}(t)|$ as a function of edge current-flow betweenness centrality are plotted on Fig.
+% The absolute values of filament states $|\vec{\lambda}(t)|$ as a function of edge current-flow betweenness centrality are plotted on Fig.
 \ref{fig:v_lam_cent}, colored by corresponding conductance.
@@
 
-\paragraph{Voltage distribution}
-
-Voltage distribution on junctions $|\vec{V_e}|(t)$ as a function of centrality is also included in fig.
-\ref{fig:v_lam_cent}.
+% \paragraph{Voltage distribution} 
+As the network is being activated, junctions with higher centralities are more likely to exhibit higher voltages and filament states.
+Voltage ($\vec{V_e}$) and filament state ($\vec{\lambda}$) are strongly coupled on the junctions; higher voltage on a junction will lead to faster growth of its filament state.
+In return, a higher filament state means the junction will have a higher conductance (\textbf{refer to equation here}), and an increased chance to reach higher voltage.
+Voltage distribution on junctions $|\vec{V_e}|(t)$ as a function of centrality at $t = 1.7$s is plotted in fig.
+\ref{fig:v_snapshot} where the color code represents each junction's corresponding conductance.
 The data points can be clearly classified into three regimes: The two linear regimes at the left and right ends correspond to the OFF and ON junctions.
@@
 	\centering
-	\includegraphics[width=0.5\linewidth]{figure/v_lam_cent}
-	\caption{Absolute values of voltage and filament as a function of centrality at T = ??
+	\includegraphics[width=0.9\linewidth]{figure/v_snapshot.png}
+	\caption{Figure details not finalized yet.}
+	\label{fig:v_snapshot}
+\end{figure}
+
+% \begin{figure}[h]
+% 	\centering
+% 	\includegraphics[width=0.5\linewidth]{figure/v_lam_cent}
+% 	\caption{Absolute values of voltage and filament as a function of centrality at T = ??
 s.
@@
 Maybe junction on time will be a more obvious metric.}}
-	\label{fig:v_lam_cent}
-\end{figure}
+% 	\label{fig:v_lam_cent}
+% \end{figure}
 
-\paragraph{Current flow}
-\textbf{Not sure if we have  to keep this}
-The cumulative current flow through nanowires shows a linear relationship with node current flow betweenness centrality. 
-% fig. \ref{fig:i_cent}.
+% \paragraph{Current flow}
+% \textbf{Not sure if we have  to keep this}
+% The cumulative current flow through nanowires shows a linear relationship with node current flow betweenness centrality. 
+% % fig. \ref{fig:i_cent}.
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\linewidth]{figure/I_cent}
-	\caption{Current flow on a nanowire vs node centrality}
-	\label{fig:i_cent}
-\end{figure}
+% \begin{figure}[h]
+% 	\centering
+% 	\includegraphics[width=0.5\linewidth]{figure/I_cent}
+% 	\caption{Current flow on a nanowire vs node centrality}
+% 	\label{fig:i_cent}
+% \end{figure}
 
@@
 \begin{figure}[h]
+	\begin{subfigure}[b]{0.5\textwidth}
 		\centering
-	\includegraphics[width=0.5\linewidth]{figure/in_TE}
-	\caption{\textbf{Might not need color here.
+		\includegraphics[width=1\linewidth]{figure/in_TE.png}
+
+	\end{subfigure}
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width = 1\linewidth]{figure/nbc_TE.png}
+	\end{subfigure}
+
+	\caption{\textbf{Choose one of them (maybe both).
+Might not need color here.
 Node in-TE as a function of centrality.

### 2020-06-10 main.tex

--- 2020-06-10 main.tex
@@
 \textbf{Include some explanation about the network's activation under DC signal. And the fact most of the analysis are done with snapshots.}
-
-\textbf{Talk about the sim settings and the network being used.}
 
@@
 Fig.
-\ref{fig:TE_cent_act} shows the in-TE vs closeness centrality around the time of formation of winner-takes-all current path ($T = ..$ here).
+\ref{fig:in_te} shows the in-TE vs closeness centrality around the time of formation of winner-takes-all current path ($T = ..$ here).
 On a semi-logy scale, the high centrality nodes exhibit high TE and communicability.
@@
 
-Furthermore, fig.
+% Furthermore, fig.
 \ref{fig:EC_AIS} suggests that junctions with higher betweenness centralities tend to have lower active information storage (AIS) and will be turned on relatively earlier.
@@
 Use the cite command for an inline citation, e.g.
-\cite{Hao:gidmaps:2014}.
 
@@
 
-Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.
-
 \end{document}

### 2020-06-11 main.tex
recent work on results

@@
-\documentclass[fleqn,10pt,  amsmath,amssymb,aps]{wlscirep}
+\documentclass[fleqn,10pt,  reprint, amsmath,amssymb,aps, floatfix]{wlscirep}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{subcaption}
+\usepackage{bm}% bold math
+\usepackage{bbold}
 
@@
 As the network activates, junctions at more central locations in the network evolve faster.
-A winner-takes-all (WTA) current path \textbf{Cite Dublin paper} form at the most central nodes first, followed by additional current paths branch out to the rest of the network.
+A winner-takes-all (WTA) current path \textbf{(Cite Dublin paper)} form at the most central nodes first, followed by additional current paths branch out to the rest of the network.
 At a specific time $t$, current-flow betweenness centrality of junctions is determined by Eq.
@@
 Junctions with higher centrality are more likely to receive higher voltage.
-Voltage ($\vec{V_e}$) and conductance are strongly coupled on the junctions; higher voltage on a junction leads to faster evolution of its conductantce state.
+Voltage ($\vec{V_e}$) and conductance are strongly coupled on the junctions; higher voltage on a junction leads to faster evolution of its conductance state.
 In return, a higher conductance state means the junction is more likely to receive a higher voltage (\textbf{refer to equation here}).\textbf{[ZK: I think it's more complex than this due to topology - the voltage distribution changes adaptively in response to junction state changes.]}
@@
 
-Voltage distribution on junctions $|\vec{V_e}|(t)$ as a function of centrality at $t = 1.7$s is plotted in Fig.
+Voltage distribution on junctions $|\vec{V}_e|(t)$ as a function of centrality at $t = 1.7$s is plotted in the left panel of Fig.
 \ref{fig:ebc+nw} where the color code represents each junction's corresponding conductance.
@@
 \textbf{(Have to write equations to define in and out)}.
-With 50 repetitions of different source/target node pairings (while the graphical distance in between is kept constant), TE averaged across the whole time-series shows a close-to-linear relationship with centrality on a semi-logy scale in Fig.
-\ref{fig:in_te}.
-Centrality here is calculated at $t = 0\,$s, and therefore reflects the influence of the structural properties of the network (as all junctions have equal weights at $t = 0$s).
-Nodes at more central positions have the potential to send out and take in more information and exhibit richer dynamics (\textbf{might have to explain about "richer"}).
+Simulations of the same 100-nanowire network's activation subject to Mackey-Glass signal with 50 different source-drain pairings (the graphical distance in-between is kept constant) are performed.
+In-TE averaged across the whole time-series for all nodes in these 50 simulations are plotted in the left panel of Fig.
+\ref{fig:TE_combined} with respect to the corresponding closeness centrality.
+The closeness centrality is calculated at $t = 0\,$s to reflect the structural properties of the network's topology since the weights on all edges are equal.
+The color code represents the communicability of nodes at $t = 0\,$s \textbf{(might not need it, ref to COMM equation if necessary.)}.
+A close-to-linear relationship can be observed on semi-logy scale, where the dashed red line stands for the best fit.
+Nodes at more central positions have the potential to send out and take in more information and exhibit richer dynamics.
+(\textbf{might have to explain about "richer"}).
 
-Fig.
-\ref{fig:in_te} shows the in-TE vs closeness centrality around the time of formation of winner-takes-all current path ($T = ..$ here).
-On a semi-logy scale, the high centrality nodes exhibit high TE and communicability.
-At $T = ..$, these nodes are connected to junctions that are already turned ON.
-On the other hand, the group at the left of the figure consists of low centrality nodes \textbf{[Alon - i feel like a sentence is missing explaining this, and connecting to the next sentence]}.
-Within this regime, nodes with higher centralities are more likely to have larger TE.
-The transition from low TE to high TE with respect to centrality increase validates the analysis in fig.
-\ref{fig:in_te}.
+Right panel of Fig.
+\ref{fig:TE_combined} shows the in-TE vs closeness centrality when approaching the WTA path formations in those 50 simulations.
+A time window of $0.2 \,$s is employed to capture the local information dynamics.
+The centrality and communicability are measured at the WTA formations.
+In comparison with the left panel of Fig.
+\ref{fig:TE_combined}, the centralities at the WTA formations span to a wider range, where the high centrality nodes are the ones connected to junctions that are turned ON.
+On the other hand, the group at the left of the figure consists of low centrality nodes, whose adjacent junctions are still OFF.
+\textbf{[Alon - i feel like a sentence is missing explaining this, and connecting to the next sentence]} Within this regime, nodes with higher centralities are more likely to have larger TE.
+The transition from low TE to high TE with respect to centrality increase validates analysis of the left panel - higher centralities will lead to richer information dynamics.
 
@@
 	\centering
-	\includegraphics[width=0.45\linewidth]{figure/in_TE}
-	\includegraphics[width=0.45\linewidth]{figure/TE_cent_act}
+	% \includegraphics[width=0.45\linewidth]{figure/in_TE}
+	% \includegraphics[width=0.45\linewidth]{figure/TE_cent_act}
+	\includegraphics[width=0.9\linewidth]{figure/TE_combined}
 	\caption{\textbf{Might not need color here.
@@
 	\textbf{Intrinsic property of the network that does not have any dynamics. We have structural information here.}}
-	\label{fig:in_te}
+	\label{fig:TE_combined}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.5\linewidth]{figure/time_series}
+	\includegraphics[width=0.3\linewidth]{figure/time_series}
+	\includegraphics[width=0.6\linewidth]{figure/time_align}
 	\caption{\textbf{Time series data for network measures.} The dashed vertical green line represents the 			time of first current path formation.
@@
 			\textbf{Gaussian -linear inter, KSG - nonlinear, sensitive}}
+
+	\caption{\textbf{Key events time as functions of first current path formation time.} 
+			The same 100 network is used for 50 simulations with different source-drain pairings.
+The graphical distances between sources and drains are controlled to be constant.
+Identical Mackey-Glass signal with random amplitudes ranging between 2-5 V are applied to these simulations.
+Simulations with higher amplitudes will form current paths earlier.
+			\newline 
+			X-axis represents the current path formation time in different simulations.
+Y-axis represents the corresponding time for key events to take place in these simulations.
+As shown in this figure, key events such as $\Delta G$ maximum, TE spike (in Gaussian estimation) and modularity drop will happen around the first current path formation time.
+			\newline
+			\textbf{Rephrase here} Thus the network will be optimal for information processing and specific task around the transition phase when the first current path is forming and the network is turning on.
+}
 	\label{fig:time_series}
@@
 \paragraph{Network time series.}
+
+\textbf{Need to discuss about how to divide the regimes in a rigorous/ quantitative way.}
 Time series analysis of the network's activation can be even more intriguing.
@@
 
-\textbf{Show the regimes on figure.}
-
 The transition regime ends when most junctions are at high-conductance states (the rest are not reachable with this specific source-drain pairing).
 Collective conductance will be stable at a high level.
-Information flow will decrease to a lower scale similar to the resting regime.
-The modularity will also be stable in this regime.
+Information flow decreases to a lower scale similar to the resting regime.
+The modularity remains stable in this regime as well.
 
@@
 Nodes are colored with the sum of inTE and outTE averaged in the last $0.2\,$s time window.
-Similarly, junctions are colored by the sum of the TE flows in both direction in the last $0.2 s$ time window.
-(Kraskov estimator is used here.) At $t= 0.5 s$, the whole network is at rest.
+Similarly, junctions are colored by the sum of the TE flows in both direction in the last $0.2\,$s time window.
+(Kraskov estimator is used here.) At $t= 0.5 \,$s, the whole network is at rest.
 None of the nodes or junctions are having significant information transfer.
-When the first current path is formed at $t = 1.465 s$, some nodes and junctions start to have significant information flow, but most flows are happening around the central nodes.
-When $t = 2.0 s$, the information flow is even stronger as more nodes are having high in and out TEs.
+When the WTA path is formed at $t = 1.465 \,$s, the central region is having significant information flow.
+When $t = 2.0 \,$s, the information flow is even stronger as more nodes are having high in and out TEs.
 Meanwhile, even nodes at peripheral positions are having significant information flow.
-After the network is in the equilibrium regime for a while ($t = 2.5 s$), the information flows decay as the local TE values are significantly lower than the transition regime.
+After the network enters the equilibrium regime ($t = 3 \,$s), the information flows decay as the local TE values are significantly lower than the transition regime.
 
-\begin{figure}[]
-	\centering
-	\includegraphics[width=0.5\linewidth]{figure/time_align}
-	\caption{\textbf{Key events time as functions of first current path formation time.} 
-			The same 100 network is used for 50 simulations with different source-drain pairings.
+% \begin{figure}[]
+% 	\centering
+% 	\includegraphics[width=0.5\linewidth]{figure/time_align}
+% 	\caption{\textbf{Key events time as functions of first current path formation time.} 
+% 			The same 100 network is used for 50 simulations with different source-drain pairings.
 The graphical distances between sources and drains are controlled to be constant.
@@
 Simulations with higher amplitudes will form current paths earlier.
-			\newline 
-			X-axis represents the current path formation time in different simulations.
+% 			\newline 
+% 			X-axis represents the current path formation time in different simulations.
 Y-axis represents the corresponding time for key events to take place in these simulations.
 As shown in this figure, key events such as $\Delta G$ maximum, TE spike (in Gaussian estimation) and modularity drop will happen around the first current path formation time.
-			\newline
-			\textbf{Rephrase here} Thus the network will be optimal for information processing and specific task around the transition phase when the first current path is forming and the network is turning on.
+% 			\newline
+% 			\textbf{Rephrase here} Thus the network will be optimal for information processing and specific task around the transition phase when the first current path is forming and the network is turning on.
 }
-	\label{fig:time_align}
-\end{figure}
+% 	\label{fig:time_align}
+% \end{figure}
 
-\begin{figure*}[]
+\begin{figure*}[h]
 	\centering
@@
 The times when the key events take place are recorded and plotted as fig.
-\ref{fig:time_align}.
+\ref{fig:time_series}.
 \textbf{Wording HERE} With the current path formation time on the x-axis, times for other key events line up fairly well.
@@
 \paragraph{Network pre--activation -- memory capacity and learning}
+
 \textbf{Why we care about different initial states?} 
@@
 
-The same 100-nanowire network is activated with Mackey-Glass signal.(\textbf{Ref here}) The states of the network at different stages during the activation process are extracted and employed as initial states for benchmarks tasks.
+To achieve different pre-activation levels, the same 100-nanowire network is activated with Mackey-Glass signal.
+The states of the network through the activation are extracted every 10 time step ($0.01 \,$s) and employed as initial states for benchmarks tasks.
 Memory capacity and non-linear transformation are used to test the network's performance at different activation levels (details in method part).
@@
 Fig.
-\ref{fig:benchmark} (a) shows the memory capacity of the network with respect to different initial states (\textbf{explain different initial states}).
-The tests with pre-activation between 1 to 2 seconds are showing significantly better performance compared to the rest.
-The average active information storages corresponding to these tests are shown in fig.
+\ref{fig:benchmark} (a) shows the memory capacity of the network with respect to pre-activation length and the average active information storages corresponding to these tests are shown in fig.
 \ref{fig:benchmark} (c).
-The states with better performance are exhibiting higher active information storage during the tests.
-Since memory capacity of the network is indicating its capability of short term memory, higher MC coincide with higher AIS is not surprising.
+The tests with pre-activation length between $1-2 \,$ s are showing significantly better performance compared to the rest.
+These pre-activated states with better performance are exhibiting higher active information storage during the tests as well.
+Moreover, the pre-activation length of these states coincides with the network's transition regime subject to Mackey-Glass signal, which is indicating that the network is optimal for memory capacity around its activation.
 
 Meanwhile, fig.
-\ref{fig:benchmark} (b) shows the non-linear transformation performance with different pre-activated states.
-Similar to the results in MC tests, the states with 1 to 2 seconds of pre-activation perform better than others.
-However, with roughly around 1.5 seconds of pre-activation, the performance experience a notable drop, which could be caused by the formation of the first current path.
-As the degree of freedom of voltage distribution is low (\textbf{Need to work on this}) when the first current path is forming.
-The averaged transfer entropy in non-linear transformation tests is shown in fig.
+\ref{fig:benchmark} (b) shows the non-linear transformation (NLT) performance with different pre-activated states.
+Similar to the results in the MC tests, the states with $1-2 \,$ s of pre-activation perform better than others.
+However, with $~1.5 \,$s of pre-activation, the performance experience a notable drop, which could be caused by the formation of the first current path.
+As the network's voltage distribution obtain more linearity when the first current path is forming.
+But the NLT test requires certainly level of degree of freedom (non-linearity) to achieve better performance.
+The averaged transfer entropy in NLT tests is shown in fig.
 \ref{fig:benchmark} (d).
 The better performing states show correspondence with higher averaged transfer entropy.
-Non-linear transformation test requires certainly level of degree of freedom to achieve relatively good performance.
-According to \textbf{TE equation}, those higher TE tests are exhibiting stronger information dynamics, which is mainly caused by the complexity and uncertainty of voltage distribution.
-Thus better NLT performance can be explained by higher transfer entropy values in those tests.
+The result in NLT indicates that the network is also prime for learning around its activation.
+
+% According to \textbf{TE equation}, those higher TE tests are exhibiting stronger information dynamics, which is mainly caused by the complexity and uncertainty of voltage distribution.
 
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{figure/mpl_plot}
+	\includegraphics[width=0.45\linewidth]{figure/mpl_plot}
+	\includegraphics[width=0.45\linewidth]{figure/graph_plot}
 	\caption{}
-	\label{fig:mpl_plot}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.8\linewidth]{figure/graph_plot}
-	\caption{}
-	\label{fig:graph_plot}
+	\label{fig:nws}
 \end{figure}
@@
 In this section the network's states at different activation stages are extracted and used as initial states for benchmarking.
-Starting from these pre-activated states, memory capacity of the network is measured to estimate the network's ability of reconstructing its short-term memory \textbf{Cite Jaeger}.
-Non-linear transformation is used to test the network's learning ability \textbf{Cite Kevin}.
+Starting from these pre-activated states, memory capacity of the network is measured to estimate the network's ability of reconstructing its short-term memory \textbf{(Cite Jaeger)}.
+Non-linear transformation is used to test the network's learning ability \textbf{(Cite UCLA)}.
 

### 2020-06-25 main.tex
edits from Zdenka. Include my recent stuff and computing resources.

@@
 \usepackage{bbold}
+
+%%% user-defined macros
+\newcommand{\Vj}{V_{\rm j}}
+\newcommand{\cNB}{c_{\scriptscriptstyle \rm NB}}
+\newcommand{\cEB}{c_{\scriptscriptstyle \rm EB}}
+\newcommand{\gtapprox}{\raisebox{-0.5ex}{$\,\stackrel{>}{\scriptstyle \sim}\,$}}
+\newcommand{\ltapprox}{\raisebox{-0.5ex}{$\,\stackrel{<}{\scriptstyle \sim}\,$}}
+%%%
 
@@
 
-\textbf{Include some explanation about the network's activation under DC signal. And the fact most of the analysis are done with snapshots.}
-
-\textbf{ZK: The first para can be a short preamble to briefly introduce the network model (referring to methods for details) and describe the numerical experiments presented below (without yet mentioning the results.
+\textbf{Include some explanation about the network's activation under DC signal.
+And the fact most of the analysis are done with snapshots.
+ZK: The first para can be a short preamble to briefly introduce the network model (referring to methods for details) and describe the numerical experiments presented below (without yet mentioning the results.
 Return to this after Results section draft is done.}
@@
 As the network activates, junctions at more central locations in the network evolve faster.
-A winner-takes-all (WTA) current path \textbf{(Cite Dublin paper)} form at the most central nodes first, followed by additional current paths branch out to the rest of the network.
+A winner-takes-all (WTA) current path \textbf{(Cite Dublin paper) ZK: and Maass 2000, On the computational power of WTA} form at the most central nodes first, followed by additional current paths branch out to the rest of the network.
 At a specific time $t$, current-flow betweenness centrality of junctions is determined by Eq.
@@
 % Voltage distribution on junctions $|\vec{V_e}|(t)$ as a function of centrality is also included in fig.
-\ref{fig:ebc+nw}.
+\ref{fig:ebc_nw}.
 The data points can be clearly classified into three regimes: The two linear regimes at the left and right ends correspond to the OFF and ON junctions.
@@
 
-Voltage distribution on junctions $|\vec{V}_e|(t)$ as a function of centrality at $t = 1.7$s is plotted in the left panel of Fig.
-\ref{fig:ebc+nw} where the color code represents each junction's corresponding conductance.
-The data points can be clearly classified into three regimes: The two linear regimes at the left and right ends correspond to the OFF and ON junctions.
-The transition regime in the middle consists of the junctions whose conductance are in transient between low and high \textbf{[Alon -  wording here doesn't sound right][Ru - I guess still need some suggestions here]}.
-Within each regime, junctions with higher centrality will have higher voltage.
-Earlier current paths consist of these higher centrality junctions.
+The distribution of voltage magnitude across junctions $|\Vj|(t)$ as a function of edge betweenness centrality $\cEB (t)$ at $t = 1.7$s is shown in Fig.~\ref{fig:ebc_nw} (left panel), with color indicating each junction's conductance state.
+Three regimes can be clearly identified: (i) an extensive linear regime spanning approximately 4 orders of magnitude in both $\Vj$ and $\cEB$ characterized by low conductance ($\ltapprox 10^{-6}\,$S) states, corresponding to junctions in an "OFF" state; (ii) a shorter transition regime with intermediate conductance values ($10^{-4} - 10^{-5}\,$S), corresponding to junctions in the tunneling regime; and (iii) a short linear regime characterized by high conductance ($\gtapprox 10^{-5}\,$S) states, corresponding to junctions that have switched "ON" and carry current.
+%Within each regime, junctions with higher centrality will have higher voltage. Earlier current paths consist of these higher centrality junctions.
 
-The right panel of Fig.
-\ref{fig:ebc+nw} shows the corresponding snapshot of the network at $t = 1.7\,$s.
-The WTA pathway formed earlier (at $t = 1.465 \,$s) is represented by orange nodes.
-The edges are colored based on their corresponding conductance in log scale.
-The positions of high-conductance junctions beside the WTA pathway demonstrate the importance of centrality - the junctions at more central positions are turned on earlier.
+The right panel of Fig.~\ref{fig:ebc_nw} shows the corresponding snapshot of the network graph at $t = 1.7\,$s.
+The orange nodes indicate the first current transport path, formed earlier at $t = 1.465 \,$s.
+This WTA path coincides with the shortest path length between the source and drain nodes.
+The edges are colored based on their corresponding conductance using the same log scale as in the $\Vj - \cEB$ plot.
+The locations of high-conductance junctions beside the WTA pathway demonstrate the importance of centrality -- junctions at more central locations switch on earlier and thus regulate the subsequent dynamics of information spread by current.
+This clearly demonstrates how the interplay between network topology and junction dynamics results in adaptive information flow.
 
@@
 %	\includegraphics[width=0.5\linewidth]{figure/v_lam_cent}
-	\includegraphics[width=0.8\linewidth]{figure/ebc+nw}
+	\includegraphics[width=0.8\linewidth]{figure/ebc_nw}
 	\caption{Left -- Voltage magnitude and conductance across network junctions as a function of their current betweenness centrality at $t = 1.7\,$s.
-Right -- corresponding snapshot of network graph, showing the first current path (between orange nodes) established earlier, at $t = 1.7\,$s.
-Dashed edges denote junctions still in an "off" (high resistance) state.}
-	\label{fig:ebc+nw}
+Right -- corresponding snapshot of network graph, showing the first current path (between orange nodes) established earlier, at $t = 1.465\,$s.
+Edge colour denotes junction conductance state.}
+	\label{fig:ebc_nw}
 \end{figure}
@@
 \paragraph{Transfer entropy -- information exchange.}
-The node closeness centrality also shows an interesting correlation with transfer entropy.
+The node betweenness centrality $\cNB$ shows an interesting correlation with transfer entropy.
 For any node in the network, the out-TE is considered as the average transfer entropy measured from the node to its neighbors.
@@
 Simulations of the same 100-nanowire network's activation subject to Mackey-Glass signal with 50 different source-drain pairings (the graphical distance in-between is kept constant) are performed.
-In-TE averaged across the whole time-series for all nodes in these 50 simulations are plotted in the left panel of Fig.
-\ref{fig:TE_combined} with respect to the corresponding closeness centrality.
+In-TE averaged across the whole time-series for all nodes in these 50 simulations are plotted in the left panel of Fig.~\ref{fig:TE_combined} with respect to the corresponding closeness centrality.
 The closeness centrality is calculated at $t = 0\,$s to reflect the structural properties of the network's topology since the weights on all edges are equal.
-The color code represents the communicability of nodes at $t = 0\,$s \textbf{(might not need it, ref to COMM equation if necessary.)}.
-A close-to-linear relationship can be observed on semi-logy scale, where the dashed red line stands for the best fit.
+Each data point represent one node (nanowire) in one simulation of the network, with the color representing the average switched ON time of all edges connected to this node.
+A close-to-linear relationship can be observed on log-log scale, where the dashed red line stands for the best fit \textbf{might need a fitting line}.
 Nodes at more central positions have the potential to send out and take in more information and exhibit richer dynamics.
@@
 
-Right panel of Fig.
-\ref{fig:TE_combined} shows the in-TE vs closeness centrality when approaching the WTA path formations in those 50 simulations.
+Right panel of Fig.~\ref{fig:TE_combined} shows the in-TE vs betweennnes centrality when approaching the WTA path formations in those 50 simulations with the same color code.
 A time window of $0.2 \,$s is employed to capture the local information dynamics.
-The centrality and communicability are measured at the WTA formations.
-In comparison with the left panel of Fig.
-\ref{fig:TE_combined}, the centralities at the WTA formations span to a wider range, where the high centrality nodes are the ones connected to junctions that are turned ON.
+The centralities are measured exactly at the WTA formations.
+In comparison with the left panel of Fig.~\ref{fig:TE_combined}, the centralities at the WTA formations span to a wider range, and split to two groups based on $\cNB$.
+For nodes in the low centrality group (left), TE show a similar close-to-linear relation with $\cNB$ on a log-log scale.
+In addition, edges connected to higher centrality nodes are typically switched ON earlier.
+Nodes in the high centrality group (right) normally exhibit higher TE when approaching the WTA formation.
+Since $\cNB$ is calculated based on the current flow, the big leap in-between is mainly caused by the conductance jump of edges switched ON.
+
+% where the high centrality nodes are the ones connected to junctions that are switched ON.
 On the other hand, the group at the left of the figure consists of low centrality nodes, whose adjacent junctions are still OFF.
@@
 	\centering
-	\includegraphics[width=0.3\linewidth]{figure/time_series}
-	\includegraphics[width=0.6\linewidth]{figure/time_align}
+	\includegraphics[width=0.5\linewidth]{figure/time_series}
+% 	\includegraphics[width=0.6\linewidth]{figure/time_align}
 	\caption{\textbf{Time series data for network measures.} The dashed vertical green line represents the 			time of first current path formation.
@@
 
-	\caption{\textbf{Key events time as functions of first current path formation time.} 
-			The same 100 network is used for 50 simulations with different source-drain pairings.
+% 	\caption{\textbf{Key events time as functions of first current path formation time.} 
+% 			The same 100 network is used for 50 simulations with different source-drain pairings.
 The graphical distances between sources and drains are controlled to be constant.
@@
 Simulations with higher amplitudes will form current paths earlier.
-			\newline 
-			X-axis represents the current path formation time in different simulations.
+% 			\newline 
+% 			X-axis represents the current path formation time in different simulations.
 Y-axis represents the corresponding time for key events to take place in these simulations.
 As shown in this figure, key events such as $\Delta G$ maximum, TE spike (in Gaussian estimation) and modularity drop will happen around the first current path formation time.
-			\newline
-			\textbf{Rephrase here} Thus the network will be optimal for information processing and specific task around the transition phase when the first current path is forming and the network is turning on.
+% 			\newline
+% 			\textbf{Rephrase here} Thus the network will be optimal for information processing and specific task around the transition phase when the first current path is forming and the network is turning on.
 }
@@
 
-\textbf{Need to discuss about how to divide the regimes in a rigorous/ quantitative way.}
 Time series analysis of the network's activation can be even more intriguing.
-Fig.
-\ref{fig:time_series}(a) shows the network's collective conductance (\textbf{maybe network conductance}) time-series.
-The activation of the network mainly have three regimes - the resting (\textbf{maybe another word} ?ground ?low-conductance) regime, the transition regime and the stable (?equilibrium JOEL ?high-conductance) regime.
-Key events during the activation coincide with each other as a function of time.
+Fig.~\ref{fig:time_series}(a) shows the network's collective conductance (\textbf{maybe network conductance}) time-series.
+The activation of the network mainly have three regimes: pre-activation, activation and post-activation.
+Moreover, key events in the activation regime coincide with each other as a function of tiem.
 
-In the resting regime, all junctions are OFF.
+In the pre-activation regime (shaded red in Fig.~\ref{fig:time_series}), all junctions are OFF.
 Collective conductance of the network remains low.
@@
 
-(Refer to \ref{fig:time_series}) The transition regime starts when the first junctions is turned on (\textbf{Here it's the tunneling model so maybe some other wording.
+As shaded green area in Fig.~\ref{fig:time_series}, the activation regime starts when the first junctions is turned on (\textbf{Here it's the tunneling model so maybe some other wording.
 Like some switches are exhibiting higher conductance}).
 Collective conductance of the network starts to increase significantly as the time derivative will have a spike.
-(\textbf{Connect spikes to formation of pathways???
-Have to check.
-Not sure if a clear connection exists.}) Modularity of the network reaches the bottom level \textbf{wording here}.
-With more junctions turned ON, the first current path (winner-takes-all) will be formed and the conductance keeps increasing with a lower path.
+Modularity of the network reaches the bottom level \textbf{wording here, maybe minimum}.
+With more junctions turned ON, the first current path (WTA) will be formed and the conductance keeps increasing with a lower path.
 Modularity starts to increase again as the nodes on the current path stands out from the rest of the network.
@@
 
-The transition regime ends when most junctions are at high-conductance states (the rest are not reachable with this specific source-drain pairing).
+The activation regime ends when most junctions are at high-conductance states (the rest are not reachable with this specific source-drain pairing).
 Collective conductance will be stable at a high level.
@@
 
+\textbf{Might not need this paragraph, or move to supplementary.}
 A more thorough validation of the hypothesis is done activating the same network with different source-drain pairings.
@@
 
-\begin{figure*}[]
+\begin{figure}[]
 	\centering
@@
 	\caption{\textbf{Benchmarks of the network with different initial states.} The network's voltage distribution and junction filament states are extracted every 10 time-step during the activation with a Mackey-Glass signal input.
-Memory capacity/ non-linear transformation tests are then performed accordingly initiating from those pre-activated states.
+Memory capacity/ non-linear transformation tests are then performed accordingly initiating from those pre-initialized states.
 \\
@@
 	\label{fig:benchmark}
-\end{figure*}
+\end{figure}
 
-\paragraph{Network pre--activation -- memory capacity and learning}
+\paragraph{Network pre-initialization -- memory capacity and learning}
 
@@
 
-To achieve different pre-activation levels, the same 100-nanowire network is activated with Mackey-Glass signal.
+To achieve different pre-initialized levels, the same 100-nanowire network is activated with Mackey-Glass signal.
 The states of the network through the activation are extracted every 10 time step ($0.01 \,$s) and employed as initial states for benchmarks tasks.
@@
 
-Fig.
-\ref{fig:benchmark} (a) shows the memory capacity of the network with respect to pre-activation length and the average active information storages corresponding to these tests are shown in fig.
-\ref{fig:benchmark} (c).
-The tests with pre-activation length between $1-2 \,$ s are showing significantly better performance compared to the rest.
-These pre-activated states with better performance are exhibiting higher active information storage during the tests as well.
-Moreover, the pre-activation length of these states coincides with the network's transition regime subject to Mackey-Glass signal, which is indicating that the network is optimal for memory capacity around its activation.
+Fig.~\ref{fig:benchmark} (a) shows the memory capacity of the network with respect to pre-initialization length and the average active information storage corresponding to these tests are shown in Fig.~\ref{fig:benchmark} (c).
+The tests with pre-initialization length between $1-2 \,$ s are showing significantly better performance compared to the rest.
+These pre-initialized states with better performance are exhibiting higher active information storage during the tests as well.
+Moreover, the pre-initialization length of these states coincides with the network's transition regime subject to Mackey-Glass signal, which is indicating that the network is optimal for memory capacity around its activation.
 
 Meanwhile, fig.
-\ref{fig:benchmark} (b) shows the non-linear transformation (NLT) performance with different pre-activated states.
-Similar to the results in the MC tests, the states with $1-2 \,$ s of pre-activation perform better than others.
-However, with $~1.5 \,$s of pre-activation, the performance experience a notable drop, which could be caused by the formation of the first current path.
-As the network's voltage distribution obtain more linearity when the first current path is forming.
-But the NLT test requires certainly level of degree of freedom (non-linearity) to achieve better performance.
-The averaged transfer entropy in NLT tests is shown in fig.
-\ref{fig:benchmark} (d).
+\ref{fig:benchmark} (b) shows the non-linear transformation (NLT) performance with different pre-initialized states.
+Similar to the results in the MC tests, the states with $1-2 \,$ s of pre-initialization perform better than others.
+The averaged transfer entropy in NLT tests is shown in Fig.~\ref{fig:benchmark} (d).
 The better performing states show correspondence with higher averaged transfer entropy.
@@
 
+% However, with $~1.5 \,$s of pre-initialization, the performance experience a notable drop, which could be caused by the formation of the first current path.
+As the network's voltage distribution obtain more linearity when the first current path is forming.
+But the NLT test requires certainly level of degree of freedom (non-linearity) to achieve better performance.
+
+\paragraph{Computing resources} \textbf{Might move this part to discussion.}
+
+Refer to \textbf{Cramer et al.
+Criticality paper}.
+Networks with more computing resources are more likely to perform better in benchmarking tests \textbf{Need reference for computing resource}.
+In the context of nanowire network, one might presumably consider that denser networks (higher average degree) will have more computing resource.
+The same MC task \textbf{refer to }is performed on several denser networks with 100 nanowires.
+
+As shown in Fig.~ \ref{fig:computing_resource}, the general shape of these four curves indicates that networks with more junctions are performing better in the MC task.
+The performance of dense network (577 junctions) keeps high disregarding the pre-initialization length since it has more than sufficient computing resource.
+But for the other three curves, the performance is clearly priming between $1-2 \,$s, which is around their activation.
+The better performance around activation suggests that, with limited computing resource, the performance of the network would be priming around activation (criticality).
+Or oppositely, to tune a network for better performance, the most efficient way is to drive it around it's critical point.
+
+\begin{figure}
+    \centering
+	\includegraphics[width=0.5\linewidth]{figure/computing_resource.png}
+	\caption{\textbf{Place holder} Computing resource plot}
+	\label{fig:computing_resource}
+\end{figure}
 % According to \textbf{TE equation}, those higher TE tests are exhibiting stronger information dynamics, which is mainly caused by the complexity and uncertainty of voltage distribution.
@@
 \subsection*{\label{sec:level2} Simulation}
-When connected to external voltage biases, nanowire networks behave like traditional electrical networks.
-Each component in the network obeys Kirchhoff's law.
-Hence the voltage distribution across the network can be obtained by solving (\cite{Dorfler2018}):
+Under an applied voltage bias, nanowire networks behave like conventional electrical networks, with each component obeying Kirchhoff's law.
+Hence, at each instant of time the voltage distribution across the network is obtained by solving \cite{Dorfler2018}
 
 \begin{equation}
-{\cal L}^\dagger V = I,
+{\cal L}^\dagger V = I \qquad ,
 \end{equation}
 
-where $\mathcal{L}^\dagger$ is the expanded graph Laplacian of the network, composed as:
+where $\mathcal{L}^\dagger$ is the expanded graph Laplacian of the network, expressed in block matrix representation as
 
@@
 	\end{array}
-	\right],
+	\right] \qquad ,
 \end{equation}
 
-in which $\cal L$ is the graph Laplacian and $C$ represents the nodes (wires) connected to external electrodes.
+where $\cal L$ is the graph Laplacian and $C$ represents the nodes (wires) connected to external electrodes. The Laplacian is
 
 \begin{equation}
-{\cal L} = D - W.
+{\cal L} = D - W \qquad ,
 \end{equation}
 
-Here $W$ is the weighted adjacency matrix of the network. The weights on edges are determined based on their conductance:
+where $W$ is the weighted adjacency matrix of the network, with edge weights based on conductance,
 \begin{equation}
-	\mathbf W_{ij} = \mathbf A_{ij} G(i,j).
+	\mathbf W_{ij} = \mathbf A_{ij} G(i,j) \qquad ,
 \end{equation}
 
-And $D$ is the weighted degree matrix generated from $W$:
-\begin{align}
-	d_i = \sum \limits_{k=1}^{N} \mathbf W_{i,k},\\
-	\mathbf D = \textbf{diag}(d_i).
-\end{align}
+and where $D$ is the weighted degree matrix generated from $W$:
+\begin{equation}
+		 D = \textbf{diag}(d_i) \qquad , \qquad d_i = \sum \limits_{k=1}^{N} \mathbf W_{i,k} \qquad .
+\end{equation}
+
+\textbf{[ZK: to discuss -- matrix notation]}
 
 \subsection*{Centrality}
-Centrality \textbf{Put some reference here} is an important measure that helps understand the fundamental structures and connectivities of networks.
+\textbf{[ZK: I would put this first sentence in results.
+In methods, we can just jump straight into describing what we did.]}Centrality \textbf{Put some reference here} is an important measure that helps understand the fundamental structures and connectivities of networks.
 Betweenness centrality of nodes and edges in networks can demonstrate ....
@@
 
-A variation of centrality measures based on current flow model proposed by Brandes and Fleischer \cite{Brandes2005} is employed here.
-As the electrical dynamics in our networks fall in the class of \textbf{random walks} (not sure about here).
-
-The betweenness centrality of a edge in the networks can be determined by:
-
+Here, we use a variation of centrality measures based on current flow proposed by Brandes and Fleischer \cite{Brandes2005}.
+%As the electrical dynamics in our networks fall in the class of \textbf{random walks} (not sure about here).
+The current betweenness centrality of an edge in the network is defined as
 \begin{equation}
-c_{CB}(e) = \frac{\sum \limits_{s \neq t \in V}\tau_{st}(e)}{(n-1)(n-2)},
+c_{CB}(e) = \frac{\sum \limits_{s \neq t \in N}\tau_{st}(e)}{(n-1)(n-2)},
 \label{eq:ebc}
 \end{equation}
-
-where $\tau_{st}(e)$ is the current flow through edge $e$ between nodes $s$ and $t$, while $n$ stands for number of nodes in the network.
-
-The closeness centrality of a node in this context is structured in the same way as normal closeness centrality, with distance measured based on effective resistance rather than graphical distance.
-Therefore it is given by:
-
+where $\tau_{st}(e)$ is the current flow through edge $e$ between nodes $s$ and $t$ and $n$ is the number of nodes in the network.
+The current closeness centrality of a node is structured in the same way as the usual closeness centrality, with the distance measure based on effective resistance rather than graphical distance:
 \begin{equation}
-	c_{CC}(v) = \frac{n-1}{\sum \limits_{v \neq w \in V} R(v,w)}.
+	c_{CC}(n) = \frac{n-1}{\sum \limits_{v \neq w \in N} R(v,w)} \qquad ,
 	\label{eq:ecc}
 \end{equation}
-In the context of a unit $st$-current in the network, $R(v,w)$ represents the effective resistance between nodes $v$ and $w$.
+%In the context of a unit $st$-current in the network,
+where $R(v,w)$ is the effective resistance between nodes $v$ and $w$.
 
 \subsection*{Communicability}
+
+\textbf{No communicability results anymore. So might just delete this part.}
 Communicability in a network represents .... \cite{Estrada2008}.
 
-In this work communicability is calculated based on the weighted connections \cite{Crofts2009}.
-A symmetric matrix $\mathbf M$ is generated to depict the communicability distribution, where $\mathbf M_{ij}$ represents the communicability between nodes $i$ and $j$.
-Therefore, $\mathbf M$ reads:
+In this study, communicability is calculated based on the weighted connections \cite{Crofts2009}.
+A symmetric matrix $\mathbf M$ is generated to depict the communicability distribution, where $\mathbf M_{ij}$ represents the communicability between nodes $i$ and $j$: \textbf{[ZK: to discuss - do we use bf for matrix and normal font for matrix elemeent?]}
 \begin{equation}
@@
 \end{equation} 
-
-The communicability of a node can be defined as how communicable the node is to the rest of the network, which will have the expression as:
-
+The communicability of a node can then be defined as how communicable the node is to the rest of the network:
 \begin{equation}
-	m_i = \sum \limits_{k = 1}^N \mathbf M_{ik}, \qquad k \neq i.
+	m_i = \sum \limits_{j = 1}^N \mathbf M_{ij} \;, \qquad j \neq i \; .
 	\label{eq:ncomm}
@@
 \subsection*{Modularity}
-Modularity is a network metric that ..... \textbf{talk about it here} \cite{Rubinov2009}.
+Modularity is a network metric that ..... \textbf{talk about it here -- ZK: move to results} \cite{Rubinov2009}.
 
-Recent studies in neuro-science demonstrated that modularity plays an important role in .... \textbf{talk about it here} \cite{Godwin2015}.
+Recent studies in neuro-science demonstrated that modularity plays an important role in .... \textbf{talk about it here -- ZK: move to results} \cite{Godwin2015}.
 
-Modularity ($\mathbf Q^w$) in a weighted network can be calculated by the Louvain method \cite{Blondel2008}:
+Modularity in a weighted network can be calculated by the Louvain method \cite{Blondel2008}:
 
@@
 \end{equation}
-
-in which $w_{i,j}$ is the weight of the edge between nodes $i$ and $j$, $I^w$ represents sum of all weights in the network, $k_i^w$ stands for the weighted degree of node $i$, $m_i$ is the community where node $i$ is located, and $\delta$ is the Kronecker delta function.
+where $W_{ij}$ is the weight of the edge between nodes $i$ and $j$, %$I^w$ represents sum of all weights in the network, $k_i^w$ stands for the weighted degree of node $i$,
+$m_i$ is the community where node $i$ is located, and $\delta$ is the Kronecker delta function.
 
@@
 
-\subsection*{Benchmark}
+\subsection*{Benchmarkmarking Tasks}
 
-Regular reservoir computing realizations are typically initialized with homogeneous or randomly generated states.
-The system then evolves based on specific tasks.
+%In reservoir computing applications, networks are typically initialized with homogeneous or randomly generated edge states.
+The system then evolves according to specific tasks.
 \textbf{WHY we want different initial states?}
 
-A nanowire network enters different stages during its activation.
-Its states at different stages typically have different voltage distribution, unevenly grew filament states and therefore diverse conductance levels.
-In this section the network's states at different activation stages are extracted and used as initial states for benchmarking.
-Starting from these pre-activated states, memory capacity of the network is measured to estimate the network's ability of reconstructing its short-term memory \textbf{(Cite Jaeger)}.
-Non-linear transformation is used to test the network's learning ability \textbf{(Cite UCLA)}.
+A nanowire network evolves through different global states before, during and after activation.
+At the local junction level, these states are characterized by dynamically changing conductance levels due to continuous voltage redistribution and unevenly growing filament states.
+To investigate the information processing performance of different global states, two benchmark reservoir computing tasks were implemented on the network.
+After activating the network with the Mackey-Glass signal, the states at different time points before, during and after activation were extracted and used as initial states for the two benchmarking tasks: memory capacity and non-linear transformation.
 
-A randomly generated time series from uniform distribution in the interval $[-2,2]$ is used as the input signal for memory capacity test.
-A linear combination of the network's state at $t$ (node voltage) is applied to reconstruct the previous input at $t - k$.
-$k = 1 ...
-100$ are used to investigate different delayed intervals.
-The $k-$delay memory capacity is defined as:
+Memory capacity (MC) is a measure of the network's ability to recall information from its fading memory property \textbf{(Cite Jaeger)}. 
+A randomly generated time series from uniform distribution in the interval $[-2,2]$ is used as the input signal.
+A linear combination of the network's state (node voltage) at $t$ is applied to reconstruct the previous input at $t - k$.
+Using $k = 1 ...
+100$ to include different delayed intervals, MC is defined as
+%The $k-$delay memory capacity is defined as:
 \begin{equation}
-	\text{MC}_k = \dfrac{\text{cov}^2(\mathbf u_{t-k}, \mathbf o_t)}{\sigma^2 (\mathbf u_{t-k}) \sigma^2 (\mathbf o_t)}.
+	\text{MC} = \sum \limits_{k=1}^\infty \text{MC}_k
+	\; , \mbox{with} \; 
+	\text{MC}_k = \dfrac{\text{cov}^2(\mathbf u_{t-k}, \mathbf o_t)}{\sigma^2 (\mathbf u_{t-k}) \sigma^2 (\mathbf o_t)} \; .
 \end{equation}
-The generic memory capacity for the network can thus be calculated as:
-\begin{equation}
-	\text{MC} = \sum \limits_{k=1}^\infty \text{MC}_k.
-\end{equation}
+where ....
+% The generic memory capacity for the network can thus be calculated as:
+% \begin{equation}
+% 	\text{MC} = \sum \limits_{k=1}^\infty \text{MC}_k.
+% \end{equation}
 
-The non-linear transformation task makes use of sinusoidal wave as the input signal and try to transfer the signal to other periodic signals in the shape of square or sawtooth.
-Similar to memory capacity test, linear combinations of the network's states are done to fit the target signal.
-The accuracy is calculated by $1 - \text{RNMSE}$:
+Non-linear transformation tests the network's learning ability \textbf{(Cite UCLA)}.
+An input sinusoidal wave is transformed by the network into either a square or sawtooth waveform.
+Similar to the MC test, linear combinations of the network's states are used to fit the target signal.
+The accuracy is calculated as $1 - \text{RNMSE}$, where
 \begin{equation}
@@
 \end{equation}
+and where $Y$ is the fitting results while $O$ represents the target signal.
 
